---
title: "Gene-gene networks for ensemble of Ecoli MG1655+ models"
output: powerpoint_presentation
date: "2025-12-03"
---

# Setup

### Options for figure outputs from chuncks

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dev = "png",
  dpi = 600,
  fig.width = 5,
  fig.height = 4
)
```

### Libraries installed on r-compendia.sif singularity container

```{r, warning=F, message=F, include=F}
library(librarian)
shelf(#KEGGREST, 
      #EnrichmentBrowser,
#      ComplexHeatmap,
#      circlize,
#      RColorBrewer,
#      DESeq2,
      dplyr,
      stringr,
      corrplot,
      XML,
      xml2,
      tidyr,
      dendextend,
      GGally,
      reshape2,
      igraph,
      RCy3,
      RColorBrewer,
      gridExtra,
      Matrix,
      ggplot2)

```

```{r}
#BiocManager::install('png')
#BiocManager::install('KEGGREST')
#BiocManager::install('EnrichmentBrowser')
```

# Load data and models

This may take a while, loads ~4G of data.

* Load data and models
* Load annotations and KEGG pathways
* Gene-gene correlations


Creates the following objects:


```{r}
source("2025_12_03_setup_ec_nets.R")
source("2025_12_03_plot_funs_ec_nets.R")
```


# Make Nets

Gene-gene nets can show correlation results with visual interpretation:

- edge weight is gene-gene correlation in the data matrix or model weights
- node color is e value from homolog mapping
- node outline is whether gene is in pathway being plotted

## Genes of interest

```{r}
# hits from Elodie's screen
neb_hits <- c(
  'E4PD_hit1' = '11997cc26382b2c286cd502685a104a5_6310',
  'ABCtransporter_hit2a' = 'e0ba967783ad45e29471d6259beaaa64_7636',
  'ABCtransporter_hit2b' = 'e0ba967783ad45e29471d6259beaaa64_7638',
  'pyrG_hit3' = '11997cc26382b2c286cd502685a104a5_5994',
  'rudS_hit4' = 'ad3da1d6c4c50fc5db002d664d7b0802_4675',
  'DNAbinding_hit5' = 'e0ba967783ad45e29471d6259beaaa64_7630',
  'ECF_hit6' = 'e0ba967783ad45e29471d6259beaaa64_7632',
  'ecfT_hit7' = 'e0ba967783ad45e29471d6259beaaa64_7634',
  #'phoA' = '11997cc26382b2c286cd502685a104a5_840',
  #'pstB' = '11997cc26382b2c286cd502685a104a5_8026',
  'fepA' = '11997cc26382b2c286cd502685a104a5_1272'
  )

neb_hits_cat <- name_cat[neb_hits]
```


```{r, fig.height = 15, fig.width = 15}
de_genes <- neb_hits_cat
plot_net(de_genes, edges, ec_anns,0.15)
```

## Seed one gene at a time

```{r, fig.height = 8, fig.width = 8, warning=FALSE}

t <- lapply(c(1:(length(neb_hits_cat))), function(x){ #
  
  de_genes <- neb_hits_cat[x]

  # png(paste0(paste(paste0("/work/gd134/ec_nets/ensemble_",names(neb_hits)[x]), m, sep = "_"),".png"),
  #     res= 300,
  #     height = 8,
  #     width = 8,
  #     units = "in")
  plot_net(de_genes, edges, ec_anns,0.15)
  #dev.off()
  
  # png(paste0(paste(paste(paste0("/work/gd134/ec_corrplot/ensemble_",names(neb_hits)[x]), m, sep = "_"), neb_hits_cat[x], sep = "_"),"_corrplot.png"),
  #     res= 300,
  #     height = 4,
  #     width = 8,
  #     units = "in")
  
  plot_net_mat(de_genes, edges, ec_anns,0.15)
  #dev.off()
  
})

```

## Plot correlations of first 100 genes

```{r}
genes <- c(1:100)

corr_compare(genes, ec_anns, 'ld') # 'n', 'ld'
```


## Plot correlations of uncharacterized genes

```{r}
genes <- unchar_genes

corr_compare(genes, ec_anns, 'ld') # 'n', 'ld'
```


# For cytoscape

```{r}
t <- for_cytoscape(ec_model_corrs,"ec_ens_mg1655plus_for_cyto.csv",0)
```


# Check ranges

```{r}
t <- lapply(c(1), function(x){
  par(mfrow=c(2,1))
  range(ec_comp_corr[ec_comp_corr < 1])
  range(ec_model_corrs[[x]][ec_model_corrs[[x]] < 1])
  hist(ec_comp_corr)
  hist(ec_model_corrs[[x]])
})
```

# Operon Correlations

```{r}
ops <- unique(unlist(lapply(ec_anns_mg1655$Transcription.Units, 
                            function(x) str_split(x, " // "))))
ops <- ops[! ops == ""]
```


```{r}

opes_list <- lapply(ops, function(x){
  genes <- unlist(sapply(c(1:nrow(ec_anns_mg1655)), function(g){
    if(str_detect(ec_anns_mg1655$Transcription.Units[g], x)){
      TRUE
    }else{FALSE}
  }))
  gene_acc <- sapply(ec_anns_mg1655$Accession.1[genes], function(g) unlist(str_split(g, " // ")))
  gene_acc
})
names(opes_list) <- ops
```


```{r}
opes_corrs_model <- lapply(opes_list, function(x){
  genes_temp <- unlist(x)
  genes_temp <- name_cat_mg1655[genes_temp]
  genes_temp <- genes_temp[genes_temp %in% rownames(ec_model_corrs[[1]])]

  corr_temp <- ec_model_corrs[[1]][genes_temp,genes_temp]
  corr_temp[lower.tri(corr_temp)] <- 0
  corr_temp[abs(corr_temp) > 0 & corr_temp < 1]
})

opes_corrs_comp <- lapply(opes_list, function(x){
  genes_temp <- unlist(x)
  genes_temp <- name_cat_mg1655[genes_temp]
  genes_temp <- genes_temp[genes_temp %in% rownames(ec_comp_corr)]
  
  corr_temp <- ec_comp_corr[genes_temp,genes_temp]
  corr_temp[lower.tri(corr_temp)] <- 0
  corr_temp[abs(corr_temp) > 0 & corr_temp < 1]
})
```



```{r}
nopes_corrs_both <- lapply(opes_list, function(x){
  genes_temp <- unlist(x)
  genes_temp <- name_cat_mg1655[genes_temp]
  genes_temp <- genes_temp[genes_temp %in% rownames(ec_model_corrs[[1]])]
  rand_genes <- sample(setdiff(rownames(ec_model_corrs[[1]]),genes_temp), length(genes_temp))
  
  corr_temp <- ec_model_corrs[[1]][rand_genes,rand_genes]
  corr_temp[lower.tri(corr_temp)] <- 0
  
  
  corr_temp2 <- ec_comp_corr[rand_genes,rand_genes]
  corr_temp2[lower.tri(corr_temp2)] <- 0
  
  list(corr_temp2[(abs(corr_temp2) > 0) & (corr_temp2 < 1)], 
       corr_temp[(abs(corr_temp) > 0) & (corr_temp < 1)])
})

```

```{r}
par(mfrow=c(2,2))

hist(unlist(opes_corrs_comp), xlim = c(-1,1))
hist(unlist(opes_corrs_model), xlim = c(-1,1))

hist(unlist(lapply(nopes_corrs_both, function(x) x[[1]])), xlim = c(-1,1))
hist(unlist(lapply(nopes_corrs_both, function(x) x[[2]])), xlim = c(-1,1))

```

```{r}
all_corrs <- c(opes_corrs_comp,lapply(nopes_corrs_both, function(x) x[[1]]),
                                     opes_corrs_model,lapply(nopes_corrs_both, function(x) x[[2]]))
op_corr_df <- data.frame("operon" = rep(ops,4),
                         "corrs_med" = sapply(all_corrs, function(x) median(x)),
                         "corrs_mu" = sapply(all_corrs, function(x) mean(x)),
                         "opnop" = rep(rep(c("operon", "random"), each=length(ops)),2),
                         "df" = c(rep("compendium", length(ops)*2), rep("model", length(ops)*2))
)

g <- ggplot(op_corr_df, aes(x = corrs_med, fill = opnop, color = opnop)) +
  geom_histogram(aes(y = ..density..), alpha = 0.25) +
  geom_density(alpha = 0.5, fill = NA) +
  facet_grid(df ~ . ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_bw()
g

```

```{r}
g <- ggplot(op_corr_df, aes(x = corrs_mu, fill = opnop)) +
  geom_density(alpha = 0.5) +
  facet_grid(df ~ . ) +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw()
g
```

# End Stuff

```{r}
sessionInfo()
```

