---
title: "Gene-gene networks for ensemble of Ecoli MG1655+ models"
output: powerpoint_presentation
date: "2025-12-03"
---

# Setup

### Options for figure outputs from chuncks

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dev = "png",
  dpi = 600,
  fig.width = 5,
  fig.height = 4
)
```

### Libraries installed on r-compendia.sif singularity container

```{r, warning=F, message=F, include=F}
library(librarian)
shelf(stringr,
      corrplot,
      reshape2,
      igraph,
      RColorBrewer,
      Matrix,
      ggplot2)
```


# Load data and models

This may take a while, loads ~5G of data.

* Load data and models
* Load annotations and KEGG pathways
* Gene-gene correlations


```{r}
source("2025_12_03_setup_ec_nets.R")
source("2025_12_03_plot_funs_ec_nets.R")
```


# Make Nets

Gene-gene nets can show correlation results with visual interpretation:

- edge weight is gene-gene correlation in the data matrix or model weights
- node color is e value from homolog mapping
- node outline is whether gene is in pathway being plotted

## Genes of interest

* still to do: positive control genes gsbA, lptB, waaP

```{r}
# hits from Elodie's screen
neb_hits <- c(
  'E4PD_hit1' = '11997cc26382b2c286cd502685a104a5_6310',
  'ABCtransporter_hit2a' = 'e0ba967783ad45e29471d6259beaaa64_7636',
  'ABCtransporter_hit2b' = 'e0ba967783ad45e29471d6259beaaa64_7638',
  'pyrG_hit3' = '11997cc26382b2c286cd502685a104a5_5994',
  'rudS_hit4' = 'ad3da1d6c4c50fc5db002d664d7b0802_4675',
  'DNAbinding_hit5' = 'e0ba967783ad45e29471d6259beaaa64_7630', # eloD41
  'ECF_hit6' = 'e0ba967783ad45e29471d6259beaaa64_7632', # eloE
  'ecfT_hit7' = 'e0ba967783ad45e29471d6259beaaa64_7634', # eloT
  #'phoA' = '11997cc26382b2c286cd502685a104a5_840',
  #'pstB' = '11997cc26382b2c286cd502685a104a5_8026',
  'fepA' = '11997cc26382b2c286cd502685a104a5_1272'
  )

neb_hits_cat <- name_cat[neb_hits]
```

## Set threshold

```{r}
thresh = 0.15
```


## EloD operon

* still to do: gather other genes in eloD operon
* also other 0157_h7_EHEC strain-secific genes

```{r, fig.height = 15, fig.width = 15, warning=F}
de_genes <- neb_hits_cat[c(6:8)]
plot_net(de_genes, edges, ec_anns, thresh, save = F)
```


## All screen Hits

```{r, fig.height = 15, fig.width = 15, warning=F}
de_genes <- neb_hits_cat
plot_net(de_genes, edges, ec_anns, thresh, save = F)
```


## Seed one gene at a time

```{r, fig.height = 8, fig.width = 8, warning=FALSE}

t <- lapply(c(1:(length(neb_hits_cat))), function(x){ #
  
  de_genes <- neb_hits_cat[x]

  plot_net(de_genes, edges, ec_anns,thresh, save = F)

  plot_net_mat(de_genes, edges, ec_anns,thresh, save = F)

  
})

```


## Plot correlations of first 100 genes

```{r}
genes <- c(1:100)

corr_compare(genes, ec_anns, 'n') # 'n', 'ld'
```


## Plot correlations of uncharacterized genes

```{r}
genes <- unchar_genes

corr_compare(genes, ec_anns, 'n') # 'n', 'ld'
```


# For cytoscape

```{r}
#t <- for_cytoscape(ec_model_corrs,"ec_ens_mg1655plus_for_cyto.csv",0)
```


# Check ranges

```{r}
t <- lapply(c(1), function(x){
  par(mfrow=c(2,1))
  range(ec_comp_corr[ec_comp_corr < 1])
  range(ec_model_corrs[[x]][ec_model_corrs[[x]] < 1])
  hist(ec_comp_corr)
  hist(ec_model_corrs[[x]])
})
```

# Operon Correlations

```{r, warning=F, message=F}
g <- ggplot(op_corr_df, aes(x = corrs_med, fill = opnop, color = opnop)) +
  geom_histogram(aes(y = ..density..), alpha = 0.25, binwidth = 0.05) +
  geom_density(alpha = 0.5, fill = NA) +
  facet_grid(df ~ . ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_bw()
g
```

```{r, warning=F, message=F}
g <- ggplot(op_corr_df, aes(x = corrs_mu, fill = opnop)) +
  geom_density(alpha = 0.5) +
  facet_grid(df ~ . ) +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw()
g
```


# End Stuff

```{r}
sessionInfo()
```

