---
title: "2025_11_01_gen_nets_ec_e_mg1655plus"
output: powerpoint_presentation
date: "2025-11-01"
---

# Setup

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dev = "png",
  dpi = 600,
  fig.width = 5,
  fig.height = 4
)
```

```{r, warning=F, message=F, include=F}
library(librarian)
shelf(#KEGGREST, 
      #EnrichmentBrowser,
#      ComplexHeatmap,
#      circlize,
#      RColorBrewer,
#      DESeq2,
      dplyr,
      stringr,
      corrplot,
      XML,
      xml2,
      tidyr,
      dendextend,
      GGally,
      reshape2,
      igraph,
      RCy3,
      RColorBrewer,
      gridExtra,
      Matrix,
      ggplot2)
#library(KEGGREST)
#library(EnrichmentBrowser)
#library(ComplexHeatmap)
#library(circlize)
#library(RColorBrewer)
#library(DESeq2)
#library(dplyr)
#library(corrplot)
#library(ggplot2)
```

```{r}
BiocManager::install('png')
BiocManager::install('KEGGREST')
#BiocManager::install('EnrichmentBrowser')
```


```{r}
t <- read.csv("/work/gd134/adage_models/net450_100models_571_670_k=450_seed=735_ClusterByweighted_avgweight_network_ADAGE.txt", sep = "\t", skip = 2, header = F, nrows  = 6390)
```

# Load data and models


```{r}

# compendia
ec_comp <- read.csv('../data_files/ecoli_MG165plus_genome_part2_log_counts_norm_01.csv')
gpa <- read.csv('ecoli_pan_genomev3_gene_presence_absence_ann.csv', stringsAsFactors = F)
rownames(gpa) <- gpa$first_name_comp

name_cat <- paste(paste(paste(gpa$MG1655, gpa$O157_H7_EHEC, sep = "-"),
                  gpa$BL21_DE3, sep = "-"), gpa$Gene, sep = "-")
names(name_cat) <- gpa$first_name_comp


#rownames(ec_comp) <- make.unique(gpa[ec_comp$X, 'MG1655'])
rownames(ec_comp) <- make.unique(name_cat[ec_comp$X])

#ec_model_files <- list.files('../outputs/weights/', pattern = "ecoli_MG165plus_*")

ec_model_files <- list.files('/work/gd134/adage_models', pattern = "net450*")
                             
ec_models <- lapply(ec_model_files, function(x){
  m <- read.csv(paste0('/work/gd134/adage_models/',x),
                stringsAsFactors = F,
                sep = "\t", skip = 2, header = F, nrows  = 6390)
  rownames(m) <- rownames(ec_comp)
  m
}
)
  


```




# Load annotations and KEGG pathways

```{r}

ec_anns_mg1655 <- read.csv('Jessica--(MG1655)-All-genes-of-MG1655.txt',
                    header = T,
                 stringsAsFactors = F,
                 sep = '\t')
unchar_genes_mg1655 <- ec_anns_mg1655$Accession.1[ec_anns_mg1655$Characterization == "UNCHARACTERIZED"]

rownames(ec_anns_mg1655 ) <- ec_anns_mg1655$Accession.1

ec_anns_ehec <- read.csv('Jessica--(O157_H7-EHEC)-All-genes-of-E.-coli-serovar-O157_H7-str.-Sak.txt',
                    header = T,
                 stringsAsFactors = F,
                 sep = '\t')
unchar_genes_ehec <- ec_anns_ehec$Accession.1[ec_anns_ehec$Characterization == "UNCHARACTERIZED"]

ec_anns_bl21de3 <- read.csv('Jessica--(BL21-DE3)-All-genes-of-E.-coli-BL21(DE3).txt',
                    header = T,
                 stringsAsFactors = F,
                 sep = '\t')
unchar_genes_bl21de3 <- ec_anns_bl21de3$Accession.1[ec_anns_bl21de3$Characterization == "UNCHARACTERIZED"]


comp_genes_pool <- unique(unlist(lapply(rownames(ec_comp), function(x) (str_split(x,'-' )))))

no_mg1655 <- rownames(ec_comp)[sapply(rownames(ec_comp), function(x) unlist(str_split(x,'-' ))[1] == "NA")]
name_cat_unchar <- rownames(ec_comp)[sapply(rownames(ec_comp), function(x) unlist(str_split(x,'-' ))[1] %in% unchar_genes_mg1655)]

unchar_genes <- rownames(ec_comp)[rownames(ec_comp) %in% c(name_cat_unchar)]
unchar_genes_all <- rownames(ec_comp)[rownames(ec_comp) %in% c(name_cat_unchar, no_mg1655)]
```






# Gene-gene correlations

```{r}
corr_method <- 'pearson' # pearson, kendall, spearman
ec_comp_corr <- cor(t(ec_comp[,-1]), method = corr_method) 
rownames(ec_comp_corr)  <- rownames(ec_comp)
colnames(ec_comp_corr)  <- rownames(ec_comp)



ec_model_corrs <- lapply(ec_models, function(x){
  comp_corr <- cor(t(x), method = corr_method)
  rownames(comp_corr)  <- rownames(ec_comp)
  colnames(comp_corr)  <- rownames(ec_comp)
  comp_corr
})

```


```{r}
par(mfrow = c(1,2))

t1 <- ec_comp_corr[1:100,1:100]
t1[t1 == 1] <- 0
corrplot(t1, 
         is.corr = F,
         col.lim = c(min(t1), max(t1)),
         method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

t1 <- ec_model_corrs[[1]][1:100,1:100]
t1[t1 == 1] <- 0
corrplot(t1, 
         is.corr = F,
         col.lim = c(min(t1), max(t1)),
         method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

```


```{r}

par(mfrow = c(1,2))

t1 <- ec_comp_corr[unchar_genes,unchar_genes]
t1[t1 == 1] <- 0
corrplot(t1, 
         is.corr = F,
         col.lim = c(min(t1), max(t1)),
         method = 'color', 
         order = 'hclust', 
          tl.pos = 'n',
         diag = FALSE)

t1 <- ec_model_corrs[[1]][unchar_genes,unchar_genes]
t1[t1 == 1] <- 0
corrplot(t1, 
         is.corr = F,
         col.lim = c(min(t1), max(t1)),
         method = 'color', 
         order = 'hclust', 
          tl.pos = 'n',
         diag = FALSE)
```


















```{r}
ec_anns <- data.frame(
  row.names = rownames(ec_comp_corr),
  'Characterization' = sapply(rownames(ec_comp_corr), function(x){
    n = unlist(str_split(x,'-' ))[1]
    if( n %in% rownames(ec_anns_mg1655)){
       ec_anns_mg1655[n, 'Characterization']
    } 
    else{
       "NoMG1655"
    }
  }
  )
)
```


# For cytoscape

```{r}
ec_model_corrs_m <- melt(ec_model_corrs)




m <- as.matrix(ec_model_corrs[[1]])
m[lower.tri(m)] <- 0
t <- triu(m)

ec_model_corrs_m <- melt(m)

ec_model_corrs_m_u <- ec_model_corrs_m[abs(ec_model_corrs_m$value) > 0 & 
                                         abs(ec_model_corrs_m$value) < 1,]

colnames(ec_model_corrs_m_u) <- c("gene1","gene2","corr")

#write.csv(ec_model_corrs_m_u, "ec_ens_mg1655plus_for_cyto.csv")
```



# As nets

Gene-gene nets can show correlation results with visual interpretation:

- edge weight is gene-gene correlation in the data matrix or model weights
- node color is e value from homolog mapping
- node outline is whether gene is in pathway being plotted

```{r}
edges <- melt(ec_model_corrs[[1]])
colnames(edges) <- c('from','to','weight')
edges <- edges[edges$weight > 0.1,]
edges <- edges[edges$weight < 1,]
de_genes <- unchar_genes[c(1:30)]

de_edges <- edges[edges$weight > 0.175 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]

net_edges <- net_edges[!net_edges$from == net_edges$to,]
```

```{r}
#unique(ec_anns$Characterization)

my_palette <- colorRampPalette(c("blue", "white", "red", "black"))(n = 5)
names(my_palette) <- unique(ec_anns$Characterization)[c(2,4,3,1,5)]

g <- graph_from_data_frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight * 20)-10

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})



node.colors <- ec_anns[vertex_attr(g, 'name'), "Characterization"]
V(g)$color <- my_palette[node.colors]

gnames <- ec_anns[vertex_attr(g, 'name'),'Common.Name']

plot(g, 
     vertex.label = NA, 
     vertex.frame.color = bd)
```

```{r}
ceb <- cluster_edge_betweenness(g) 
```

```{r, fig.height = 15, fig.width = 15}
plot(ceb, g, 
     vertex.label = gnames, 
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
```




## Gene of interest


```{r}

neb_hits <- c(
  'E4PD_hit1' = '11997cc26382b2c286cd502685a104a5_6310',
  'ABCtransporter_hit2a' = 'e0ba967783ad45e29471d6259beaaa64_7636',
  'ABCtransporter_hit2b' = 'e0ba967783ad45e29471d6259beaaa64_7638',
  'pyrG_hit3' = '11997cc26382b2c286cd502685a104a5_5994',
  'rudS_hit4' = 'ad3da1d6c4c50fc5db002d664d7b0802_4675',
  'DNAbinding_hit5' = 'e0ba967783ad45e29471d6259beaaa64_7630',
  'ECF_hit6' = 'e0ba967783ad45e29471d6259beaaa64_7632',
  'ecfT_hit7' = 'e0ba967783ad45e29471d6259beaaa64_7634',
  #'phoA' = '11997cc26382b2c286cd502685a104a5_840',
  #'pstB' = '11997cc26382b2c286cd502685a104a5_8026',
  'fepA' = '11997cc26382b2c286cd502685a104a5_1272'
  )

neb_hits_cat <- name_cat[neb_hits]

```


```{r}
edges <- melt(ec_model_corrs[[1]])
colnames(edges) <- c('from','to','weight')
edges <- edges[edges$weight > 0,]
edges <- edges[edges$weight < 1,]
de_genes <- neb_hits_cat[1]

de_edges <- edges[edges$weight > 0.15 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]

net_edges <- net_edges[!net_edges$from == net_edges$to,]
```

```{r}
#unique(ec_anns$Characterization)

my_palette <- colorRampPalette(c("blue", "white", "red", "black"))(n = 5)
names(my_palette) <- unique(ec_anns$Characterization)[c(2,4,3,1,5)]

g <- graph_from_data_frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight * 20)-10

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})



node.colors <- ec_anns[vertex_attr(g, 'name'), "Characterization"]
V(g)$color <- my_palette[node.colors]

gnames <- ec_anns[vertex_attr(g, 'name'),'Common.Name']

plot(g, 
     vertex.label = NA, 
     vertex.frame.color = bd)
```

```{r}
ceb <- cluster_edge_betweenness(g) 
```

```{r, fig.height = 20, fig.width = 20}
plot(ceb, g, 
     vertex.label = gnames, 
     col = vertex_attr(g, 'color'), 
     vertex.label.color = "black",
     vertex.size = 5,
     mark.coly = brewer.pal(n = 8, name = "Set3"))
```





## Save many pngs

```{r}
edges <- melt(ec_model_corrs[[1]])
colnames(edges) <- c('from','to','weight')
edges <- edges[edges$weight > 0,]
edges <- edges[edges$weight < 1,]
```


```{r, fig.height = 8, fig.width = 8, warning=FALSE}
lapply(c(1), function(m){
  
  edges <- melt(ec_model_corrs[[m]])
  colnames(edges) <- c('from','to','weight')
  edges <- edges[edges$weight > 0,]
  edges <- edges[edges$weight < 1,]


  lapply(c(1:(length(neb_hits_cat))), function(x){ #
  de_genes <- neb_hits_cat[x]
  de_edges <- edges[edges$weight > 0.15 & (edges$from %in% de_genes | edges$to %in% de_genes),]
  net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
  net_edges <- de_edges
  net_edges <- net_edges[!is.na(net_edges$from),]
  net_edges <- net_edges[!net_edges$from == net_edges$to,]
  #rownames(ec_anns) <- ec_anns$Accession.1
  
  my_palette <- colorRampPalette(c("blue", "white", "red", "black"))(n = 5)
  names(my_palette) <- unique(ec_anns$Characterization)[c(2,4,3,1,5)]
  
  g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
  E(g)$width <-  ((net_edges$weight - min(net_edges$weight) ) / (max(net_edges$weight) - min(net_edges$weight))) * 10  #(net_edges$weight * 20)-15
  
  bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})
  
  
  
  node.colors <- ec_anns[vertex_attr(g, 'name'), "Characterization"]
  V(g)$color <- my_palette[node.colors]
  
  gnames <- ec_anns[vertex_attr(g, 'name'),'Common.Name']
  gnames <- str_sub(gnames, "_", "\n")
  
  ceb <- cluster_edge_betweenness(g) 
#plot(g, 
#     vertex.label = gnames, 
#     col = vertex_attr(g, 'color'), 
#     vertex.label.color = "black",
#     vertex.size = 10,
#     mark.coly = brewer.pal(n = 8, name = "Set3"))
  name_temp <- vertex_attr(g, 'name')
  vertex_attr(g, 'name') <- str_replace_all(name_temp, "-","\n")
  png(paste0(paste(paste0("/work/gd134/ec_nets/ensemble_",names(neb_hits)[x]), m, sep = "_"),".png"),
      res= 300,
      height = 8,
      width = 8,
      units = "in")
plot(g, 
     #vertex.label = gnames, 
     col = vertex_attr(g, 'color'), 
     vertex.label.color = "black",
     vertex.size = 20,
     mark.coly = brewer.pal(n = 8, name = "Set3"))
  dev.off()
})
})
```







```{r, fig.height = 5, fig.width = 8, warning=FALSE}
lapply(c(1), function(m){
  
  edges <- melt(ec_model_corrs[[m]])
  colnames(edges) <- c('from','to','weight')
  #edges <- edges[edges$weight > 0,]
  edges <- edges[edges$weight < 1,]


  lapply(c(1:(length(neb_hits_cat))), function(x){ #
  de_genes <- neb_hits_cat[x]
  
  de_edges <- edges[edges$weight > 0.15 & (edges$from %in% de_genes | edges$to %in% de_genes),]
  net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
  net_edges <- de_edges
  net_edges <- net_edges[!is.na(net_edges$from),]
  net_edges <- net_edges[!net_edges$from == net_edges$to,]

  #my_palette <- colorRampPalette(c("purple", "white", "darkorange", "black"))(n = 8)
  #names(my_palette) <- unique(ec_anns$Characterization)[c(2,1,7,5,4,3,8,6)]
  
  g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)

  
  gnames <- ec_anns[vertex_attr(g, 'name'),'Common.Name']
  

  g_temp <- vertex_attr(g, 'name')
  
  t1 <- ec_comp_corr[g_temp,g_temp]
  t1[t1 == 1] <- 0
  rownames(t1) <- g_temp
  colnames(t1) <- g_temp

  t2 <- ec_model_corrs[[m]][g_temp,g_temp]
  t2[t2 == 1] <- 0
  rownames(t2) <- g_temp
  colnames(t2) <- g_temp

  png(paste0(paste(paste(paste0("/work/gd134/ec_corrplot/ensemble_",names(neb_hits)[x]), m, sep = "_"), neb_hits_cat[x], sep = "_"),"_corrplot.png"),
      res= 300,
      height = 4,
      width = 8,
      units = "in")
  
  par(mfrow = c(1,2))

corrplot(t1, 
         is.corr = F,
         #title = neb_hits_cat[x], #paste(names(neb_hits)[x], neb_hits[x]),
         col.lim = c(min(t1), max(t1)),
         method = 'color', 
         order = 'hclust', #'original', 
          tl.pos = 'ld',
         type = "lower",
         tl.cex = .5,
         tl.col = "black",
         cl.cex = .3,
         title = "gene expression",
          mar = c(0,0,4,0),
         diag = FALSE)


corrplot(t2, 
         is.corr = F,
         col.lim = c(min(t2), max(t2)),
         method = 'color', 
         order = 'hclust', #'original', 
          tl.pos = 'ld',
         type = "lower",
         tl.cex = .5,
         tl.col = "black",
         cl.cex = .3,
         title = "model",
          mar = c(0,0,4,0),
         diag = FALSE)

  dev.off()
})
})
```

```{r}
range(ec_comp_corr[ec_comp_corr < 1])
range(ec_model_corrs[[1]][ec_model_corrs[[1]] < 1])

lapply(c(1), function(x){
range(ec_model_corrs[[x]][ec_model_corrs[[x]] < 1])
})
```


```{r}
lapply(c(1), function(x){
  par(mfrow=c(2,1))
hist(ec_comp_corr)
hist(ec_model_corrs[[x]])
})

```

# Operon Correlations


```{r}
ops <- unique(unlist(lapply(ec_anns_mg1655$Transcription.Units, 
                            function(x) str_split(x, " // "))))
ops <- ops[! ops == ""]
```


```{r}

opes_list <- lapply(ops, function(x){
  genes <- unlist(sapply(c(1:nrow(ec_anns_mg1655)), function(g){
    if(str_detect(ec_anns_mg1655$Transcription.Units[g], x)){
      TRUE
    }else{FALSE}
  }))
  gene_acc <- sapply(ec_anns_mg1655$Accession.1[genes], function(g) unlist(str_split(g, " // ")))
  gene_acc
})
names(opes_list) <- ops
```


```{r}
opes_corrs_model <- lapply(opes_list, function(x){
  genes_temp <- unlist(x)
  genes_temp <- name_cat_mg1655[genes_temp]
  genes_temp <- genes_temp[genes_temp %in% rownames(ec_model_corrs[[1]])]

  corr_temp <- ec_model_corrs[[1]][genes_temp,genes_temp]
  corr_temp[lower.tri(corr_temp)] <- 0
  corr_temp[abs(corr_temp) > 0 & corr_temp < 1]
})

opes_corrs_comp <- lapply(opes_list, function(x){
  genes_temp <- unlist(x)
  genes_temp <- name_cat_mg1655[genes_temp]
  genes_temp <- genes_temp[genes_temp %in% rownames(ec_comp_corr)]
  
  corr_temp <- ec_comp_corr[genes_temp,genes_temp]
  corr_temp[lower.tri(corr_temp)] <- 0
  corr_temp[abs(corr_temp) > 0 & corr_temp < 1]
})
```



```{r}
nopes_corrs_both <- lapply(opes_list, function(x){
  genes_temp <- unlist(x)
  genes_temp <- name_cat_mg1655[genes_temp]
  genes_temp <- genes_temp[genes_temp %in% rownames(ec_model_corrs[[1]])]
  rand_genes <- sample(setdiff(rownames(ec_model_corrs[[1]]),genes_temp), length(genes_temp))
  
  corr_temp <- ec_model_corrs[[1]][rand_genes,rand_genes]
  corr_temp[lower.tri(corr_temp)] <- 0
  
  
  corr_temp2 <- ec_comp_corr[rand_genes,rand_genes]
  corr_temp2[lower.tri(corr_temp2)] <- 0
  
  list(corr_temp2[(abs(corr_temp2) > 0) & (corr_temp2 < 1)], 
       corr_temp[(abs(corr_temp) > 0) & (corr_temp < 1)])
})

```

```{r}
par(mfrow=c(2,2))

hist(unlist(opes_corrs_comp), xlim = c(-1,1))
hist(unlist(opes_corrs_model), xlim = c(-1,1))

hist(unlist(lapply(nopes_corrs_both, function(x) x[[1]])), xlim = c(-1,1))
hist(unlist(lapply(nopes_corrs_both, function(x) x[[2]])), xlim = c(-1,1))

```

```{r}
all_corrs <- c(opes_corrs_comp,lapply(nopes_corrs_both, function(x) x[[1]]),
                                     opes_corrs_model,lapply(nopes_corrs_both, function(x) x[[2]]))
op_corr_df <- data.frame("operon" = rep(ops,4),
                         "corrs_med" = sapply(all_corrs, function(x) median(x)),
                         "corrs_mu" = sapply(all_corrs, function(x) mean(x)),
                         "opnop" = rep(rep(c("operon", "random"), each=length(ops)),2),
                         "df" = c(rep("compendium", length(ops)*2), rep("model", length(ops)*2))
)

g <- ggplot(op_corr_df, aes(x = corrs_med, fill = opnop, color = opnop)) +
  geom_histogram(aes(y = ..density..), alpha = 0.25) +
  geom_density(alpha = 0.5, fill = NA) +
  facet_grid(df ~ . ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_bw()
g

```

```{r}
g <- ggplot(op_corr_df, aes(x = corrs_mu, fill = opnop)) +
  geom_density(alpha = 0.5) +
  facet_grid(df ~ . ) +
  scale_fill_brewer(palette = "Dark2") +
  theme_bw()
g
```
# End Stuff


```{r}
sessionInfo()
```

