---
title: "2023_07_11_gen_nets_sa_se_seqA_n100"
output: powerpoint_presentation
date: "2023-07-11"
---

# Setup

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dev = "png",
  dpi = 600,
  fig.width = 5,
  fig.height = 4
)
```

```{r, warning=F, message=F, include=F}
library(librarian)
shelf(KEGGREST, 
      EnrichmentBrowser,
#      ComplexHeatmap,
#      circlize,
#      RColorBrewer,
#      DESeq2,
      dplyr,
      stringr,
      corrplot,
      XML,
      xml2,
      tidyr,
      dendextend,
      GGally,
      reshape2,
      igraph,
      RColorBrewer,
      gridExtra,
      ggprism,
ggpubr,
      ggplot2)
#library(KEGGREST)
#library(EnrichmentBrowser)
#library(ComplexHeatmap)
#library(circlize)
#library(RColorBrewer)
#library(DESeq2)
#library(dplyr)
#library(corrplot)
#library(ggplot2)
library(iGraphMatch)
```

# Load data and models


```{r}

# compendia
sa_comp <- read.csv('../data_files/sa_NCTC3825_filt_norm_log_01.csv')
rownames(sa_comp) <- sa_comp$X

sa_comp_mapped <- read.csv('../data_files/se_MAPPED_sa_NCTC3825_filt_norm_log_01.csv')
rownames(sa_comp_mapped) <- sa_comp_mapped$X

se_comp <- read.csv('../data_files/se_se16_epi_comp_log_counts_norm_01.csv')
rownames(se_comp) <- se_comp$X

# TL models



postPT_model <- read.csv('../outputs/weights/prev/data_files/se_MAPPED_sa_NCTC3825_filt_norm_log_01_se16_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:tanh_init:glorot_uniform_ep:10_tied:True_batch:10_lr:0.01_prew:_postPT_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(postPT_model) <- se_comp$X



preFT_model <- read.csv('../outputs/weights/prev/data_files/se_MAPPED_sa_NCTC3825_filt_norm_log_01_se16_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:tanh_init:glorot_uniform_ep:10_tied:True_batch:10_lr:0.01_prew:_preFT_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(preFT_model) <- se_comp$X

postFT_model <- read.csv('../outputs/weights/prev/data_files/se_MAPPED_sa_NCTC3825_filt_norm_log_01_se16_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:tanh_init:glorot_uniform_ep:10_tied:True_batch:10_lr:0.01_prew:_postFT_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(postFT_model) <- se_comp$X


postPTctrl_model <- read.csv('../outputs/weights/prev/data_files/se_se16_epi_comp_log_counts_norm_01_se16_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:tanh_init:glorot_normal_ep:20_tied:True_batch:10_lr:0.01_prew:_postPT_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(postPTctrl_model) <- se_comp$X




preFTctrl_model <- read.csv('../outputs/weights/prev/data_files/se_se16_epi_comp_log_counts_norm_01_se16_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:tanh_init:glorot_normal_ep:20_tied:True_batch:10_lr:0.01_prew:_preFT_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(preFTctrl_model) <- se_comp$X

postFTctrl_model <- read.csv('../outputs/weights/prev/data_files/se_se16_epi_comp_log_counts_norm_01_se16_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:tanh_init:glorot_normal_ep:20_tied:True_batch:10_lr:0.01_prew:_postFT_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(postFTctrl_model) <- se_comp$X


# original models
seONLY_model <- read.csv('../outputs/weights/prev/data_files/se_se16_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:tanh_init:glorot_uniform_ep:20_tied:True_batch:10_lr:0.1_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(seONLY_model) <- se_comp$X


saONLY_model <- read.csv('../outputs/weights/prev/data_files/sa_NCTC3825_filt_norm_log_01_seed:571_nodes:50_kl1:0_kl2:0_act:tanh_init:glorot_uniform_ep:20_tied:True_batch:10_lr:0.01_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(saONLY_model) <- sa_comp$X

```


# Load annotations and KEGG pathways

```{r}
se16_kegg <- read.csv('../node_interpretation/se16_KEGG_format.txt',
                 stringsAsFactors = F,
                 sep = '\t')
rownames(se16_kegg) <- se16_kegg$KEGGPathID

saNCTC8325_kegg <- read.csv('../node_interpretation/saNCTC8325_KEGG_format.txt',
                 stringsAsFactors = F,
                 sep = '\t')
rownames(saNCTC8325_kegg) <- saNCTC8325_kegg$KEGGPathID
```

```{r}
se16_annotations <- read.csv('seNIHLM067.gff', 
                             stringsAsFactors = F,
                             skip = 52,
                             sep = '\t',
                             header=F)

se16_ann_tag2name <- data.frame(
  locus_tag = sapply(se16_annotations$V9, 
                            function(x) sub('locus_tag=','',
                                            str_extract(x, 'locus_tag=SE16__[0-9]*'))),
  gene_symbol = sapply(se16_annotations$V9, 
                            function(x) sub('Name=','',
                                            str_extract(x, 'Name=[a-zA-Z0-9_]*'))),
  product = sapply(se16_annotations$V9, 
                            function(x) sub('product=','',
                                            str_extract(x, 'product=[a-zA-Z0-9_ -]*')))
)
se16_ann_tag2name <- se16_ann_tag2name[!is.na(se16_ann_tag2name$product),]
rownames(se16_ann_tag2name) <- se16_ann_tag2name$locus_tag

saNCTC8325_annotations <- read.csv('NCTC8325.gff3', 
                             stringsAsFactors = F,
                             skip = 2,
                             header=F,
                             sep = '\t')

saNCTC8325_ann_tag2name <- data.frame(
  locus_tag = sapply(saNCTC8325_annotations$V9, 
                            function(x) sub('locus_tag=','',
                                            str_extract(x, 'locus_tag=SAOUHSC_[0-9Tp]*'))),
  gene_symbol = sapply(saNCTC8325_annotations$V9, 
                            function(x) sub('Name=','',
                                            str_extract(x, 'Name=[a-zA-Z0-9_]*')))
)

saNCTC8325_ann_name2product <- data.frame(
  gene_symbol = sapply(saNCTC8325_annotations$V9, 
                            function(x) sub('gene=','',
                                            str_extract(x, 'gene=[a-zA-Z0-9_]*'))),
  product = sapply(saNCTC8325_annotations$V9, 
                            function(x) sub('product=','',
                                            str_extract(x, 'product=[a-zA-Z0-9_ -]*')))
)

saNCTC8325_ann_tag2name <- saNCTC8325_ann_tag2name[!is.na(saNCTC8325_ann_tag2name$locus_tag),]
saNCTC8325_ann_name2product <- saNCTC8325_ann_name2product[!is.na(saNCTC8325_ann_name2product$product),]

saNCTC8325_ann_tag2name2 <- merge(saNCTC8325_ann_tag2name,
                                  saNCTC8325_ann_name2product,
                                  all.x = T)


rownames(saNCTC8325_ann_tag2name2) <- make.unique(saNCTC8325_ann_tag2name2$locus_tag)
```

```{r}
se_sa_map <- read.csv('se16_sa3825_map.csv',
                      stringsAsFactors = F)
```



# Gene-gene correlations

```{r}
corr_method <- 'pearson' # pearson, kendall, spearman
sa_comp_corr <- cor(t(sa_comp[,-1]), method = corr_method) 
rownames(sa_comp_corr)  <- sa_comp$X
colnames(sa_comp_corr)  <- sa_comp$X

sa_comp_mapped_corr <- cor(t(sa_comp_mapped[,-1]), method = corr_method)
rownames(sa_comp_mapped_corr)  <- sa_comp_mapped$X
colnames(sa_comp_mapped_corr)  <- sa_comp_mapped$X

se_comp_corr <- cor(t(se_comp[,-1]), method = corr_method)
rownames(se_comp_corr)  <- se_comp$X
colnames(se_comp_corr)  <- se_comp$X

postFT_model_corr <- cor(t(postFT_model), method = corr_method)
rownames(postFT_model_corr)  <- se_comp$X
colnames(postFT_model_corr)  <- se_comp$X

preFT_model_corr <- cor(t(preFT_model), method = corr_method)
rownames(preFT_model_corr)  <- se_comp$X
colnames(preFT_model_corr)  <- se_comp$X

se_model_corr <- cor(t(seONLY_model), method = corr_method)
rownames(se_model_corr)  <- se_comp$X
colnames(se_model_corr)  <- se_comp$X

sa_model_corr <- cor(t(saONLY_model), method = corr_method)
rownames(sa_model_corr)  <- sa_comp$X
colnames(sa_model_corr)  <- sa_comp$X
```

# Gene-gene correlations: Se and Sa compendia

```{r}
par(mfrow = c(1,2))

corrplot(se_comp_corr[1:2266,1:2266], 
         method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

corrplot(sa_comp_corr[1:2766,1:2766], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)
```

# Gene-gene correlations: Se and Sa compendia, first 100 genes

```{r}
par(mfrow = c(1,2))

corrplot(se_comp_corr[1:100,1:100], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

corrplot(sa_comp_corr[1:100,1:100], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)
```

# Gene-gene correlations: Sa and Sa-mapped compendia, first 100 genes
```{r}
par(mfrow = c(1,2))

corrplot(sa_comp_corr[1:100,1:100], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

corrplot(sa_comp_mapped_corr[1:100,1:100], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)
```
# Gene-gene correlations: Se and Sa-mapped compendia, first 100 genes

```{r}
par(mfrow = c(1,2))

corrplot(se_comp_corr[1:100,1:100], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

corrplot(sa_comp_mapped_corr[1:100,1:100], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)
```


# Gene-gene correlations: Se and Sa comps and models, first 100 genes

```{r}
par(mfrow = c(2,2))

corrplot(se_comp_corr[1:100,1:100], method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

corrplot(sa_comp_corr[1:100,1:100], method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

corrplot(se_model_corr[1:100,1:100], method = 'color', 
         title='S.e. model', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.pos = 'n',
         diag = FALSE)

corrplot(sa_model_corr[1:100,1:100], method = 'color', 
         title='S.a. model', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.pos = 'n',
         diag = FALSE)

```

# Gene-gene correlations: Se and Sa comps and TL models, first 100 genes

```{r}
par(mfrow = c(2,2))



corrplot(se_model_corr[1:100,1:100], method = 'color', 
         title='S.e. model', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.pos = 'n',
         diag = FALSE)

corrplot(sa_model_corr[1:100,1:100], method = 'color', 
         title='S.a. model', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.pos = 'n',
         diag = FALSE)

corrplot(postFT_model_corr[1:100,1:100], method = 'color', 
         title='S.e. model post fine-tune', 
         mar=c(0,0,1,0),
         
         tl.pos = 'n',
         order = 'original', diag = FALSE)

corrplot(preFT_model_corr[1:100,1:100], method = 'color', 
         title='S.e. model pre fine-tune', 
         mar=c(0,0,1,0),
         tl.pos = 'n',
         order = 'original', diag = FALSE)
```




# Plot by KEGG pathway

```{r}
se_2CS <- unlist(str_split(se16_kegg['map02020:Two-component system', 'Genes'],
                    pattern = ';'))
se_2CS_filt <- se_2CS[se_2CS %in%rownames(postFT_model_corr)]

sa_2CS <- unlist(str_split(saNCTC8325_kegg['sao02020:Two-component system - Staphylococcus aureus subsp. aureus NCTC8325', 'Genes'],
                    pattern = ';'))

sa_2CS_filt <- sa_2CS[sa_2CS %in%rownames(sa_model_corr)]
```


# Two-componant systems


```{r}
par(mfrow = c(2,2))

se_2CS_names <- se16_ann_tag2name[se_2CS_filt ,'gene_symbol']

se_comp_temp <- se_comp_corr[se_2CS_filt,se_2CS_filt]
rownames(se_comp_temp) <- colnames(se_comp_temp) <-  se_2CS_names

sa_comp_mapped_temp <- sa_comp_mapped_corr[se_2CS_filt,se_2CS_filt]
rownames(sa_comp_mapped_temp) <- colnames(sa_comp_mapped_temp) <-  se_2CS_names

postFT_model_temp <- postFT_model_corr[se_2CS_filt,se_2CS_filt]
rownames(postFT_model_temp) <- colnames(postFT_model_temp) <-  se_2CS_names
preFT_model_temp <- preFT_model_corr[se_2CS_filt,se_2CS_filt]
rownames(preFT_model_temp) <- colnames(preFT_model_temp) <-  se_2CS_names



corrplot(se_comp_temp, 
         method = 'color', 
         title='S.e. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.5,
         tl.col = "black",
         diag = FALSE)

sa_comp_mapped_temp[is.na(sa_comp_mapped_temp)] <- 0
corrplot(sa_comp_mapped_temp, 
         method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.5,
         tl.col = "black",
         diag = FALSE)


corrplot(postFT_model_temp, 
         title='S.e. model post fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = "black",
         tl.cex = 0.5)

corrplot(preFT_model_temp, 
         title='S.e. model pre fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = "black",
         tl.cex = 0.5)
```

# Two-componant systems

```{r}
se_path <- 'map02020:Two-component system'
sa_path <- 'sao02020:Two-component system - Staphylococcus aureus subsp. aureus NCTC8325'
plot_kegg_cors <- function(se_path, sa_path){
  
  se_2CS <- unlist(str_split(se16_kegg[se_path, 'Genes'],
                    pattern = ';'))
se_2CS_filt <- se_2CS[se_2CS %in%rownames(postFT_model_corr)]

sa_2CS <- unlist(str_split(saNCTC8325_kegg[sa_path, 'Genes'],
                    pattern = ';'))

sa_2CS_filt <- sa_2CS[sa_2CS %in%rownames(sa_model_corr)]


  par(mfrow = c(2,2))

se_2CS_names <- se16_ann_tag2name[se_2CS_filt ,'gene_symbol']

se_comp_temp <- se_comp_corr[se_2CS_filt,se_2CS_filt]
rownames(se_comp_temp) <- colnames(se_comp_temp) <-  se_2CS_names

sa_comp_mapped_temp <- sa_comp_mapped_corr[se_2CS_filt,se_2CS_filt]
rownames(sa_comp_mapped_temp) <- colnames(sa_comp_mapped_temp) <-  se_2CS_names

postFT_model_temp <- postFT_model_corr[se_2CS_filt,se_2CS_filt]
rownames(postFT_model_temp) <- colnames(postFT_model_temp) <-  se_2CS_names
preFT_model_temp <- preFT_model_corr[se_2CS_filt,se_2CS_filt]
rownames(preFT_model_temp) <- colnames(preFT_model_temp) <-  se_2CS_names



corrplot(se_comp_temp, 
         method = 'color', 
         title='S.e. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.5,
         tl.col = "black",
         diag = FALSE)

sa_comp_mapped_temp[is.na(sa_comp_mapped_temp)] <- 0
corrplot(sa_comp_mapped_temp, 
         method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.5,
         tl.col = "black",
         diag = FALSE)


corrplot(postFT_model_temp, 
         title='S.e. model post fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = "black",
         tl.cex = 0.5)

corrplot(preFT_model_temp, 
         title='S.e. model pre fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = "black",
         tl.cex = 0.5)
}

plot_kegg_cors(se_path, sa_path)
```


# Two-componant systems png

```{r}
se_path <- 'map02020:Two-component system'
sa_path <- 'sao02020:Two-component system - Staphylococcus aureus subsp. aureus NCTC8325'
plot_kegg_cors_se <- function(se_path){
  
  se_2CS <- unlist(str_split(se16_kegg[se_path, 'Genes'],
                    pattern = ';'))
se_2CS_filt <- se_2CS[se_2CS %in%rownames(postFT_model_corr)]






se_2CS_names <- se16_ann_tag2name[se_2CS_filt ,'gene_symbol']

se_comp_temp <- se_comp_corr[se_2CS_filt,se_2CS_filt]
rownames(se_comp_temp) <- colnames(se_comp_temp) <-  se_2CS_names

se_model_temp <- se_model_corr[se_2CS_filt,se_2CS_filt]
rownames(se_model_temp) <- colnames(se_model_temp) <-  se_2CS_names


postFT_model_temp <- postFT_model_corr[se_2CS_filt,se_2CS_filt]
rownames(postFT_model_temp) <- colnames(postFT_model_temp) <-  se_2CS_names
preFT_model_temp <- preFT_model_corr[se_2CS_filt,se_2CS_filt]
rownames(preFT_model_temp) <- colnames(preFT_model_temp) <-  se_2CS_names

name_safe <- sub('/','_',sub(':','_',sub(' ','_',se_path)))

png(paste(c('corrplots/cor_',name_safe,'.png'), collapse=''), res = 600, width = 5, height = 5, units = 'in')
  par(mfrow = c(2,2))

corrplot(se_comp_temp, 
         method = 'color', 
         title='S.e. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = "black",
         diag = TRUE)


corrplot(se_model_temp, 
         method = 'color', 
         title='S.e. only model', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = "black",
         diag = TRUE)


corrplot(postFT_model_temp, 
         title='S.e. model post fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = "black",
         tl.cex = 0.3)

corrplot(preFT_model_temp, 
         title='S.e. model pre fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = "black",
         tl.cex = 0.3)
dev.off()
}

plot_kegg_cors_se(se_path)
```


```{r}
se_kegg_m2 <- se16_kegg$KEGGPathID[se16_kegg$Length > 2]

t <- lapply(se_kegg_m2, function(x) plot_kegg_cors_se(x))
```




```{r}
par(mfrow = c(2,2))

se_2CS_names <- se16_ann_tag2name[se_2CS_filt ,'gene_symbol']
sa_2CS_names <- saNCTC8325_ann_tag2name2[sa_2CS_filt ,'gene_symbol']

se_model_temp <- se_model_corr[se_2CS_filt,se_2CS_filt]
rownames(se_model_temp) <- colnames(se_model_temp) <-  se_2CS_names

se_comp_temp <- se_comp_corr[se_2CS_filt,se_2CS_filt]
rownames(se_comp_temp) <- colnames(se_comp_temp) <-  se_2CS_names

sa_model_temp <- sa_model_corr[sa_2CS_filt,sa_2CS_filt]
rownames(sa_model_temp) <- colnames(sa_model_temp) <-  sa_2CS_names

sa_comp_temp <- sa_comp_corr[sa_2CS_filt,sa_2CS_filt]
rownames(sa_comp_temp) <- colnames(sa_comp_temp) <-  sa_2CS_names




corrplot(se_comp_temp, 
         method = 'color', 
         title='S.e. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.5,
         diag = FALSE)

corrplot(sa_comp_temp, 
         method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.25,
         diag = FALSE)


corrplot(se_model_temp, 
         title='S.e. model', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.cex = 0.5)

corrplot(sa_model_temp, 
         title='S.a. model', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.cex = 0.25)
```











# Tangles





```{r}
# Make 2 dendrograms, using 2 different clustering methods
homs <- sapply(se_2CS_filt,
       function(x) max(sa_comp_mapped[x,-1])) > 0

d1 <- postFT_model[se_2CS_filt,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()
d2 <- preFT_model[se_2CS_filt,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()

d3 <- d2 %>% match_order_by_labels(d1)


# Custom these kendo, and place them in a list
dl <- dendlist(
  d1 %>% 
    set("labels_col", as.numeric(homs)+1) %>%
    set("branches_lty", 1) ,
  d2 %>% 
    set("labels_col",  as.numeric(homs)+1)  %>%
    set("branches_lty", 1) 
)
 

dl  %>% entanglement

# Plot them together
tanglegram(dl, 
           common_subtrees_color_lines = TRUE, 
           common_subtrees_color_branches = TRUE,
           highlight_distinct_edges  = TRUE, 
           highlight_branches_lwd=FALSE, 
           margin_inner=7,
           lwd=2,
           match_order_by_labels = TRUE
)
```


```{r}
dl_unt <- dl %>% untangle(method = "step1side") 
dl_unt %>% entanglement
tanglegram(dl_unt, 
           common_subtrees_color_lines = TRUE, 
           common_subtrees_color_branches = TRUE,
           highlight_distinct_edges  = TRUE, 
           highlight_branches_lwd=FALSE, 
           margin_inner=7,
           lwd=2,
           match_order_by_labels = TRUE
)
```


### Tangle of compendium vs model

```{r}
rands <- sample(rownames(se_comp), 50, replace=F)
homs <- sapply(rands,
       function(x) max(sa_comp_mapped[x,-1])) > 0

d1 <- postFT_model[rands,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()
d2 <- se_comp[rands,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()

d3 <- d2 %>% match_order_by_labels(d1)


# Custom these kendo, and place them in a list
dl <- dendlist(
  d1 %>% 
    set("labels_col", as.numeric(homs)+1) %>%
    set("branches_lty", 1) ,
  d2 %>% 
    set("labels_col",  as.numeric(homs)+1)  %>%
    set("branches_lty", 1) 
)
 
dl  %>% entanglement

dl_unt <- dl %>% untangle(method = "step1side") 
dl_unt %>% entanglement
tanglegram(dl_unt, 
           common_subtrees_color_lines = TRUE, 
           common_subtrees_color_branches = TRUE,
           highlight_distinct_edges  = TRUE, 
           highlight_branches_lwd=FALSE, 
           margin_inner=7,
           lwd=2,
           main_left = "post ft ",
           main_right = "se comp",
           match_order_by_labels = TRUE
)
```

### KEGG paths

```{r}
tangle_kegg <- function(se_path){
  
  se_2CS <- unlist(str_split(se16_kegg[se_path, 'Genes'],
                    pattern = ';'))
se_2CS_filt <- se_2CS[se_2CS %in%rownames(postFT_model_corr)]


  homs <- sapply(se_2CS_filt,
       function(x) max(sa_comp_mapped[x,-1])) > 0

d1 <- postFT_model[se_2CS_filt,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()
d2 <- preFT_model[se_2CS_filt,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()

d3 <- d2 %>% match_order_by_labels(d1)


# Custom these kendo, and place them in a list
dl <- dendlist(
  d1 %>% 
    set("labels_col", as.numeric(homs)+1) %>%
    set("branches_lty", 1) ,
  d2 %>% 
    set("labels_col",  as.numeric(homs)+1)  %>%
    set("branches_lty", 1) 
)
 

dl  %>% entanglement

# Plot them together
name_safe <- sub('/','_',sub(':','_',sub(' ','_',se_path)))

png(paste(c('tangles/t_',name_safe,'.png'), collapse=''), res = 600, width = 5, height = 5, units = 'in')
  par(mfrow = c(2,2))
tanglegram(dl, 
           common_subtrees_color_lines = TRUE, 
           common_subtrees_color_branches = TRUE,
           highlight_distinct_edges  = TRUE, 
           highlight_branches_lwd=FALSE, 
           margin_inner=7,
           lwd=2,
           match_order_by_labels = TRUE
)
dev.off()
}
```

```{r}
se_kegg_m2 <- se16_kegg$KEGGPathID[se16_kegg$Length > 2]

tangles <- lapply(se_kegg_m2, function(x) tangle_kegg(x))
```


# As nets

Gene-gene nets can show correlation results with visual interpretation:

- edge weight is gene-gene correlation in the data matrix or model weights
- node color is e value from homolog mapping
- node outline is whether gene is in pathway being plotted

```{r}
edges <- melt(se_comp_corr)
edges <- melt(postFT_model_corr)
colnames(edges) <- c('from','to','weight')
edges <- edges[edges$weight > 0.4,]
de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.5 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]

net_edges <- net_edges[!net_edges$from == net_edges$to,]
```

```{r}
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight * 20)-10

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})


homs  <- sapply(vertex_attr(g, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2

node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]


plot(g, vertex.label = NA, vertex.frame.color = bd)
```

```{r}
ceb <- cluster_edge_betweenness(g) 
```

```{r}
plot(ceb, g, 
     vertex.label = NA, 
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
```


```{r}
plot_nets <- function(se_path){
se_2CS <- unlist(str_split(se16_kegg[se_path, 'Genes'],
                    pattern = ';'))
se_2CS_filt <- se_2CS[se_2CS %in%rownames(postFT_model_corr)]

de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.5 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]
net_edges <- net_edges[!net_edges$from == net_edges$to,]


my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight * 30)-29

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){'black'}else{'grey'})


homs  <- sapply(vertex_attr(g, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2

node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g) 
name_safe <- sub('/','_',sub(':','_',sub(' ','_',se_path)))

#png(paste(c('net_plots/',name_safe,'.png'), collapse=''), res = 600, width = 5, height = 5, units = 'in')
plot(ceb, g, 
     vertex.label = NA, 
     col = vertex_attr(g, 'color'), 
     vertex.frame.color = bd,
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()

names <- sapply(vertex_attr(g, 'name'), function(x) se16_ann_tag2name[x,'gene_symbol'])

#png(paste(c('net_plots/',name_safe,'_names.png'), collapse=''), res = 600, width = 5, height = 5, units = 'in')
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
    col = vertex_attr(g, 'color'), 
     vertex.frame.color = bd,
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()
}
```

```{r}
se_kegg_m2 <- se16_kegg$KEGGPathID[se16_kegg$Length > 2]

nets <- lapply(se_kegg_m2, function(x) plot_nets(x))
```

```{r}
lapply(se_kegg_m2[57], function(x) plot_nets(x))

se_path <- se_kegg_m2[57]
se_2CS <- unlist(str_split(se16_kegg[se_path, 'Genes'],
                    pattern = ';'))
se_2CS_filt <- se_2CS[se_2CS %in%rownames(postFT_model_corr)]

de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.5 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]
net_edges <- net_edges[!net_edges$from == net_edges$to,]


my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight * 30)-29

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})


homs  <- sapply(vertex_attr(g, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2

node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g) 


plot(ceb, g, 
     vertex.label = NA, 
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
```


# Michelle's stress response genes

```{r}
spoto_stress <- read.csv('spoto_stress_genes.csv', stringsAsFactors = F)
se16_tu_map <- read.csv('se16_tu3298_map.csv', stringsAsFactors = F)

spoto_stress_se16 <- sapply(spoto_stress$Tu3298.ID, function(x){
  temp <- se16_tu_map[se16_tu_map$tu3298_ID == x,]
  i <- which.min(se16_tu_map[se16_tu_map$tu3298_ID == x, 'hit_evalue'])
  temp[i, 'se16_ID']
  })

#spoto_stress_se16 <- unique(se16_tu_map$se16_ID[se16_tu_map$tu3298_ID %in% spoto_stress$Tu3298.ID])

se_2CS_filt <- spoto_stress_se16[spoto_stress_se16 %in%rownames(se_model_corr)]

```



```{r}
par(mfrow = c(2,2))

se_2CS_names <- se16_ann_tag2name[se_2CS_filt ,'gene_symbol']

se_comp_temp <- se_comp_corr[se_2CS_filt,se_2CS_filt]
rownames(se_comp_temp) <- colnames(se_comp_temp) <-  se_2CS_names

sa_comp_mapped_temp <- sa_comp_mapped_corr[se_2CS_filt,se_2CS_filt]
rownames(sa_comp_mapped_temp) <- colnames(sa_comp_mapped_temp) <-  se_2CS_names

postFT_model_temp <- postFT_model_corr[se_2CS_filt,se_2CS_filt]
rownames(postFT_model_temp) <- colnames(postFT_model_temp) <-  se_2CS_names
preFT_model_temp <- preFT_model_corr[se_2CS_filt,se_2CS_filt]
rownames(preFT_model_temp) <- colnames(preFT_model_temp) <-  se_2CS_names



corrplot(se_comp_temp, 
         method = 'color', 
         title='S.e. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)

sa_comp_mapped_temp[is.na(sa_comp_mapped_temp)] <- 0
corrplot(sa_comp_mapped_temp, 
         method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)


corrplot(postFT_model_temp, 
         title='S.e. model post fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

corrplot(preFT_model_temp, 
         title='S.e. model pre fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)
```



```{r}



homs <- sapply(se_2CS_filt,
       function(x) max(sa_comp_mapped[x,-1])) > 0

d1 <- postFT_model[se_2CS_filt,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()
d2 <- preFT_model[se_2CS_filt,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()

d3 <- d2 %>% match_order_by_labels(d1)


# Custom these kendo, and place them in a list
dl <- dendlist(
  d1 %>% 
    set("labels_col", as.numeric(homs)+1) %>%
    set("branches_lty", 1) ,
  d2 %>% 
    set("labels_col",  as.numeric(homs)+1)  %>%
    set("branches_lty", 1) 
)
 

dl  %>% entanglement

# Plot them together
name_safe <- sub('/','_',sub(':','_',sub(' ','_',se_path)))

#png(paste(c('t_','spoto_multi_stress','.png'), collapse=''), res = 600, width = 5, height = 5, units = 'in')
tanglegram(dl, 
           common_subtrees_color_lines = TRUE, 
           common_subtrees_color_branches = TRUE,
           highlight_distinct_edges  = TRUE, 
           highlight_branches_lwd=FALSE, 
           margin_inner=7,
           lwd=2,
           match_order_by_labels = TRUE
)
#dev.off()
```

## As a net with names


```{r, fig.width = 5, fig.height =5}

edges <- melt(postFT_model_corr) # use with .5
#edges <- melt(preFT_model_corr) # use with .5
#edges <- melt(se_comp_corr) # use with 0.75
#edges <- melt(sa_comp_mapped_corr) # use with 0.75
colnames(edges) <- c('from','to','weight')
edges <- edges[edges$weight > 0.4,]

de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.5 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]

net_edges <- net_edges[!net_edges$from == net_edges$to,]

my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight - min(net_edges$weight)) / (max(net_edges$weight) - min(net_edges$weight))

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})


homs  <- sapply(vertex_attr(g, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2



node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g) 

names <- sapply(vertex_attr(g, 'name'), function(x) se16_ann_tag2name[x,'gene_symbol'])
gene_set <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% se_2CS_filt){'black'}else{'NA'})
seed <- 1
set.seed(seed)
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))

set.seed(seed+1)
plot(ceb,g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))


set.seed(seed)
plot(ceb, g, 
     vertex.label = NA, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))

#png('net_spoto_multi_stress_with_names.png', res = 600, width = 5, height = 5, units = 'in')
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = .5,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()

```



```{r}
sapply(c(1:10), function(x){
  set.seed(x)
  #ceb <- cluster_edge_betweenness(g) 
plot(ceb,g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
})
```





# Save pngs
```{r}
#rownames(se16_tu_map) <- make.unique(se16_tu_map$se16_ID)
#names_tu <- sapply(vertex_attr(g, 'name'), function(x) se16_tu_map[x ,'tu3298_ID'])

names_tu <- sapply(vertex_attr(g, 'name'), function(x){
  temp <- se16_tu_map[se16_tu_map$se16_ID == x,]
  i <- which.min(se16_tu_map[se16_tu_map$se16_ID == x, 'hit_evalue'])
  temp[i, 'tu3298_ID']
  })

png('net_spoto_multi_stress_with_names_tu_06.png', res = 600, width = 5, height = 5, units = 'in')
set.seed(seed)
plot(ceb, g, 
     vertex.label = names_tu, 
     vertex.label.cex = .5,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()

goi <- c('Tu3298_108','Tu3298_116','Tu3298_181',
         'Tu3298_779','Tu3298_2157','Tu3298_116',
         'Tu3298_2208')
names_tu[!names_tu %in% goi] <- ""
png('net_spoto_multi_stress_with_names_tu_select_06.png', res = 600, width = 5, height = 5, units = 'in')
set.seed(seed)
plot(ceb, g, 
     vertex.label = names_tu, 
     vertex.label.cex = .5,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()

png('net_spoto_multi_stress_06.png', res = 600, width = 5, height = 5, units = 'in')
set.seed(seed)
plot(ceb, g, 
     vertex.label = NA, 
     vertex.label.cex = .5,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()
```

# save big png

```{r, fig.height=12, fig.width=12}


png('net_spoto_multi_stress_BIG_06.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = NA, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()


names_tu <- sapply(vertex_attr(g, 'name'), function(x){
  temp <- se16_tu_map[se16_tu_map$se16_ID == x,]
  i <- which.min(se16_tu_map[se16_tu_map$se16_ID == x, 'hit_evalue'])
  sub('Tu3298_','',temp[i, 'tu3298_ID'])
  })

png('net_spoto_multi_stress_names_tu_BIG_06.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = names_tu, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()


png('net_spoto_multi_stress_names_BIG_06.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()

png('net_spoto_multi_stress_names_se16_BIG_06.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = sub("SE16__","",names(names)), 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()
```


# nets of compendium



```{r, fig.width = 5, fig.height =5}

edges <- melt(postFT_model_corr) # use with .5
#edges <- melt(preFT_model_corr) # use with .5
edges <- melt(se_comp_corr) # use with 0.75
#edges <- melt(sa_comp_mapped_corr) # use with 0.75
colnames(edges) <- c('from','to','weight')
edges <- edges[edges$weight > 0.4,]

de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.75 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]

net_edges <- net_edges[!net_edges$from == net_edges$to,]

my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight - min(net_edges$weight)) / (max(net_edges$weight) - min(net_edges$weight))

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})


homs  <- sapply(vertex_attr(g, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2



node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g) 

names <- sapply(vertex_attr(g, 'name'), function(x) se16_ann_tag2name[x,'gene_symbol'])
gene_set <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% se_2CS_filt){'black'}else{'NA'})



sapply(c(1:10), function(x){
  set.seed(x)
  #ceb <- cluster_edge_betweenness(g) 
plot(ceb,g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
})



```


## save big png

```{r, fig.height=12, fig.width=12}
seed <- 2
set.seed(seed)

png('net_spoto_multi_stress_BIG_075_comp.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = NA, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()


names_tu <- sapply(vertex_attr(g, 'name'), function(x){
  temp <- se16_tu_map[se16_tu_map$se16_ID == x,]
  i <- which.min(se16_tu_map[se16_tu_map$se16_ID == x, 'hit_evalue'])
  sub('Tu3298_','',temp[i, 'tu3298_ID'])
  })

png('net_spoto_multi_stress_names_tu_BIG_075_comp.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = names_tu, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()


png('net_spoto_multi_stress_names_BIG_075_comp.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()

png('net_spoto_multi_stress_names_se16_BIG_075_comp.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = sub("SE16__","",names(names)), 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()
```


# Se model nets

```{r, fig.width = 5, fig.height =5}

edges <- melt(postFT_model_corr) # use with .5
#edges <- melt(preFT_model_corr) # use with .5
edges <- melt(se_comp_corr) # use with 0.75
edges <- melt(se_model_corr) # use with 0.5
#edges <- melt(sa_comp_mapped_corr) # use with 0.75
colnames(edges) <- c('from','to','weight')
edges <- edges[edges$weight > 0.4,]

de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.5 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]

net_edges <- net_edges[!net_edges$from == net_edges$to,]

my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight - min(net_edges$weight)) / (max(net_edges$weight) - min(net_edges$weight))

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})


homs  <- sapply(vertex_attr(g, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2



node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g) 

names <- sapply(vertex_attr(g, 'name'), function(x) se16_ann_tag2name[x,'gene_symbol'])
gene_set <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% se_2CS_filt){'black'}else{'NA'})



sapply(c(1:10), function(x){
  set.seed(x)
  #ceb <- cluster_edge_betweenness(g) 
plot(ceb,g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
})



```




## save big png

```{r, fig.height=12, fig.width=12}
seed <- 2
set.seed(seed)

png('net_spoto_multi_stress_BIG_05_se_mod.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = NA, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()


names_tu <- sapply(vertex_attr(g, 'name'), function(x){
  temp <- se16_tu_map[se16_tu_map$se16_ID == x,]
  i <- which.min(se16_tu_map[se16_tu_map$se16_ID == x, 'hit_evalue'])
  sub('Tu3298_','',temp[i, 'tu3298_ID'])
  })

png('net_spoto_multi_stress_names_tu_BIG_05_se_mod.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = names_tu, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()


png('net_spoto_multi_stress_names_BIG_05_se_mod.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()

png('net_spoto_multi_stress_names_se16_BIG_05_se_mod.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = sub("SE16__","",names(names)), 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()
```


# preFT model nets

```{r, fig.width = 5, fig.height =5}

edges <- melt(postFT_model_corr) # use with .5
#edges <- melt(preFT_model_corr) # use with .5
edges <- melt(se_comp_corr) # use with 0.75
edges <- melt(preFT_model_corr) # use with 0.5
#edges <- melt(sa_comp_mapped_corr) # use with 0.75
colnames(edges) <- c('from','to','weight')
edges <- edges[edges$weight > 0.4,]

de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.5 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]

net_edges <- net_edges[!net_edges$from == net_edges$to,]

my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight - min(net_edges$weight)) / (max(net_edges$weight) - min(net_edges$weight))

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})


homs  <- sapply(vertex_attr(g, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2



node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g) 

names <- sapply(vertex_attr(g, 'name'), function(x) se16_ann_tag2name[x,'gene_symbol'])
gene_set <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% se_2CS_filt){'black'}else{'NA'})



sapply(c(1:10), function(x){
  set.seed(x)
  #ceb <- cluster_edge_betweenness(g) 
plot(ceb,g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
})



```

## save big png

```{r, fig.height=12, fig.width=12}
seed <- 2
set.seed(seed)

png('net_spoto_multi_stress_BIG_05_spreFT_mod.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = NA, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()


names_tu <- sapply(vertex_attr(g, 'name'), function(x){
  temp <- se16_tu_map[se16_tu_map$se16_ID == x,]
  i <- which.min(se16_tu_map[se16_tu_map$se16_ID == x, 'hit_evalue'])
  sub('Tu3298_','',temp[i, 'tu3298_ID'])
  })

png('net_spoto_multi_stress_names_tu_BIG_05_preFT_mod.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = names_tu, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()


png('net_spoto_multi_stress_names_BIG_05_preFT_mod.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()

png('net_spoto_multi_stress_names_se16_BIG_05_preFT_mod.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = sub("SE16__","",names(names)), 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
dev.off()
```
# Low iron genes


# Michelle's stress response genes

```{r}
spoto_stress <- read.csv('spoto_stress_genes.csv', stringsAsFactors = F)

spoto_stress_df <- read.csv('spoto_gene_lists/es/spoto_8_H2O2.csv',
                         stringsAsFactors = F)

spoto_stress <- unique(spoto_stress_df$Gene_ID)

se16_tu_map <- read.csv('se16_tu3298_map.csv', stringsAsFactors = F)

spoto_stress_se16 <- sapply(spoto_stress, function(x){
  temp <- se16_tu_map[se16_tu_map$tu3298_ID == x,]
  i <- which.min(se16_tu_map[se16_tu_map$tu3298_ID == x, 'hit_evalue'])
  temp[i[1], 'se16_ID']
  })

#spoto_stress_se16 <- unique(se16_tu_map$se16_ID[se16_tu_map$tu3298_ID %in% spoto_stress$Tu3298.ID])

se_2CS_filt <- spoto_stress_se16[spoto_stress_se16 %in% rownames(se_model_corr)]

```



```{r}
par(mfrow = c(2,2))

se_2CS_names <- se16_ann_tag2name[se_2CS_filt ,'gene_symbol']

se_comp_temp <- se_comp_corr[se_2CS_filt,se_2CS_filt]
rownames(se_comp_temp) <- colnames(se_comp_temp) <-  se_2CS_names

sa_comp_mapped_temp <- sa_comp_mapped_corr[se_2CS_filt,se_2CS_filt]
rownames(sa_comp_mapped_temp) <- colnames(sa_comp_mapped_temp) <-  se_2CS_names

postFT_model_temp <- postFT_model_corr[se_2CS_filt,se_2CS_filt]
rownames(postFT_model_temp) <- colnames(postFT_model_temp) <-  se_2CS_names
preFT_model_temp <- preFT_model_corr[se_2CS_filt,se_2CS_filt]
rownames(preFT_model_temp) <- colnames(preFT_model_temp) <-  se_2CS_names



corrplot(se_comp_temp, 
         method = 'color', 
         title='S.e. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)

sa_comp_mapped_temp[is.na(sa_comp_mapped_temp)] <- 0
corrplot(sa_comp_mapped_temp, 
         method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)


corrplot(postFT_model_temp, 
         title='S.e. model post fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

corrplot(preFT_model_temp, 
         title='S.e. model pre fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)
```



```{r}



homs <- sapply(se_2CS_filt,
       function(x) max(sa_comp_mapped[x,-1])) > 0

d1 <- postFT_model[se_2CS_filt,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()
d2 <- preFT_model[se_2CS_filt,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()

d3 <- d2 %>% match_order_by_labels(d1)


# Custom these kendo, and place them in a list
dl <- dendlist(
  d1 %>% 
    set("labels_col", as.numeric(homs)+1) %>%
    set("branches_lty", 1) ,
  d2 %>% 
    set("labels_col",  as.numeric(homs)+1)  %>%
    set("branches_lty", 1) 
)
 

dl  %>% entanglement

# Plot them together
name_safe <- sub('/','_',sub(':','_',sub(' ','_',se_path)))

#png(paste(c('t_','spoto_multi_stress','.png'), collapse=''), res = 600, width = 5, height = 5, units = 'in')
tanglegram(dl, 
           common_subtrees_color_lines = TRUE, 
           common_subtrees_color_branches = TRUE,
           highlight_distinct_edges  = TRUE, 
           highlight_branches_lwd=FALSE, 
           margin_inner=7,
           lwd=2,
           match_order_by_labels = TRUE
)
#dev.off()
```

## As a net with names


```{r, fig.width = 5, fig.height =5}

edges <- melt(postFT_model_corr) # use with .5
#edges <- melt(preFT_model_corr) # use with .5
#edges <- melt(se_comp_corr) # use with 0.75
#edges <- melt(sa_comp_mapped_corr) # use with 0.75
colnames(edges) <- c('from','to','weight')
edges <- edges[edges$weight > 0.4,]

de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.6 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]

net_edges <- net_edges[!net_edges$from == net_edges$to,]

my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight - min(net_edges$weight)) / (max(net_edges$weight) - min(net_edges$weight))

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})


homs  <- sapply(vertex_attr(g, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2



node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g) 

names <- sapply(vertex_attr(g, 'name'), function(x) se16_ann_tag2name[x,'gene_symbol'])
gene_set <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% se_2CS_filt){'black'}else{'NA'})
seed <- 1
set.seed(seed)




#png('net_spoto_LFE_with_names.png', res = 600, width = 5, height = 5, units = 'in')
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = .5,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()

```


```{r, fig.height=12, fig.width=12}
seed <- 2
set.seed(seed)

#png('net_spoto_multi_stress_BIG_075_comp.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = NA, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()


names_tu <- sapply(vertex_attr(g, 'name'), function(x){
  temp <- se16_tu_map[se16_tu_map$se16_ID == x,]
  i <- which.min(se16_tu_map[se16_tu_map$se16_ID == x, 'hit_evalue'])
  sub('Tu3298_','',temp[i, 'tu3298_ID'])
  })

#png('net_spoto_multi_stress_names_tu_BIG_075_comp.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = names_tu, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()


#png('net_spoto_multi_stress_names_BIG_075_comp.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()

#png('net_spoto_multi_stress_names_se16_BIG_075_comp.png', res = 1200, width = 12, height = 12, units = 'in', bg = NA)
set.seed(seed)
plot(ceb, g, 
     vertex.label = sub("SE16__","",names(names)), 
     vertex.label.cex = 1,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()
```

# Uncharacterized gene


```{r}
se16_ann_tag2name$hyp <- sapply(se16_ann_tag2name$product, function(x) if( x == "hypothetical protein"){"hypothetical protein"}else{"characterized (named)"})

se_2CS_filt <- spoto_stress_se16[spoto_stress_se16 %in%rownames(se_model_corr)]
```



```{r}
se_model_corr_m1 <- melt(se_model_corr)
se_model_corr_m1$data <- "se_model"
se_model_corr_m2 <- melt(se_comp_corr)
se_model_corr_m2$data <- "se_comp"
se_model_corr_m3 <- melt(preFT_model_corr)
se_model_corr_m3$data <- "pt_model"
se_model_corr_m4 <- melt(postFT_model_corr)
se_model_corr_m4$data <- "ft_model"

se_model_corr_m <- do.call(rbind, list(se_model_corr_m1,se_model_corr_m2,se_model_corr_m3,se_model_corr_m4))

se_model_corr_m$Var1_hyp <- se16_ann_tag2name[se_model_corr_m$Var1, "hyp"]
se_model_corr_m$Var2_hyp <- se16_ann_tag2name[se_model_corr_m$Var2, "hyp"]

se_model_corr_m$type <- sapply(c(1:nrow(se_model_corr_m)), function(x){
  
  if((se_model_corr_m$Var1_hyp[x] == "hypothetical protein") & 
  (se_model_corr_m$Var2_hyp[x] == "hypothetical protein")){"hyp_hyp"}
  else if(xor((se_model_corr_m$Var1_hyp[x] == "hypothetical protein"), 
  (se_model_corr_m$Var2_hyp[x] == "hypothetical protein"))){"hyp_char"}
  else if((!se_model_corr_m$Var1_hyp[x] == "hypothetical protein") & 
  (!se_model_corr_m$Var2_hyp[x] == "hypothetical protein")){"char_char"}
})



```





```{r}
table(se_model_corr_m$type)
```

```{r}
g <- ggplot(se_model_corr_m[se_model_corr_m$value < 1 ,
                              c("value","type", "data")], 
            aes(x=type, y = value, color = data)) +
  geom_boxplot() +
theme_prism()
g
```




```{r}
g <- ggplot(se_model_corr_m[se_model_corr_m$value < 1 ,
                              c("value","type", "data")], 
            aes(x = value, color = type)) +
  facet_grid(.~data, scales = "free") +
  geom_histogram() +
theme_prism()
g
```


```{r}

t <- se_model_corr_m[se_model_corr_m$value > 0.6 & se_model_corr_m$value < 1,c("value","type", "data")]
table(t$type, t$data)
```


```{r}
sds <- tapply(se_model_corr_m$value, se_model_corr_m$data, FUN = function(x) quantile(x, c(.25,.5,.75,.95), na.rm=T))
sds
```

```{r}
t <- se_model_corr_m[se_model_corr_m$value > 0.31 & se_model_corr_m$value < 1,c("value","type", "data")]
table(t$type, t$data)
```

```{r}
rownames(se16_tu_map) <- make.unique(se16_tu_map$se16_ID)
se16_ann_tag2name$tu <- se16_tu_map[se16_ann_tag2name$locus_tag, "tu3298_ID"]
```


```{r}
par(mfrow = c(2,2))

se_2CS_filtp <- se16_ann_tag2name[se16_ann_tag2name$hyp == "hypothetical protein"   ,'locus_tag']
se_2CS_filtp <- se_2CS_filt[c(1:10)]

se_2CS_neib <- unlist(as.list(sapply(se_2CS_filtp, function(x){
  r <- sort(preFT_model_corr[,x], decreasing=T)
  names(r)[c(1:5)]
})))

se_2CS_filt <- c(se_2CS_filtp,se_2CS_neib)

se_2CS_names <- c(se16_ann_tag2name[se_2CS_filtp  ,'tu'],se16_ann_tag2name[se_2CS_neib  ,'hyp'])

se_comp_temp <- se_comp_corr[se_2CS_filt,se_2CS_filt]
rownames(se_comp_temp) <- colnames(se_comp_temp) <-  se_2CS_names

sa_comp_mapped_temp <- sa_comp_mapped_corr[se_2CS_filt,se_2CS_filt]
rownames(sa_comp_mapped_temp) <- colnames(sa_comp_mapped_temp) <-  se_2CS_names

postFT_model_temp <- postFT_model_corr[se_2CS_filt,se_2CS_filt]
rownames(postFT_model_temp) <- colnames(postFT_model_temp) <-  se_2CS_names
preFT_model_temp <- preFT_model_corr[se_2CS_filt,se_2CS_filt]
rownames(preFT_model_temp) <- colnames(preFT_model_temp) <-  se_2CS_names



corrplot(se_comp_temp, 
         method = 'color', 
         title='S.e. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)

sa_comp_mapped_temp[is.na(sa_comp_mapped_temp)] <- 0
corrplot(sa_comp_mapped_temp, 
         method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)


corrplot(postFT_model_temp, 
         title='S.e. model post fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

corrplot(preFT_model_temp, 
         title='S.e. model pre fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)
```




```{r, fig.width = 5, fig.height =5}

edges <- melt(postFT_model_corr) # use with .5
#edges <- melt(preFT_model_corr) # use with .5
#edges <- melt(se_comp_corr) # use with 0.75
#edges <- melt(sa_comp_mapped_corr) # use with 0.75
colnames(edges) <- c('from','to','weight')
edges <- edges[edges$weight > 0.4,]

de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.5 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]

net_edges <- net_edges[!net_edges$from == net_edges$to,]

my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight - min(net_edges$weight)) / (max(net_edges$weight) - min(net_edges$weight))

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})


homs  <- sapply(vertex_attr(g, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2



node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g) 

names <- sapply(vertex_attr(g, 'name'), function(x) se16_ann_tag2name[x,'gene_symbol'])
gene_set <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% se_2CS_filt){'black'}else{'NA'})
seed <- 1
set.seed(seed)
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))

set.seed(seed+1)
plot(ceb,g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))


set.seed(seed)
plot(ceb, g, 
     vertex.label = NA, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))

#png('net_spoto_multi_stress_with_names.png', res = 600, width = 5, height = 5, units = 'in')
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = .5,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()

```

## Summarize

```{r, fig.height=6, fig.width=6}
se_2CS_filtp <- se16_ann_tag2name[se16_ann_tag2name$hyp == "hypothetical protein"   ,'locus_tag']

dframes <- list('Se comp' = se_comp_corr,
            "Sa comp" = sa_comp_mapped_corr,
             "TL comp pre FT" = preFT_model_corr,
            "TL comp post FT" = postFT_model_corr)

se_2CS_neib <- data.frame(lapply(dframes, function(df){
  
  sapply(se_2CS_filtp, function(x){
  r <- sort(df[,x], decreasing=T)
  names <- names(r)[c(1:10)]
  sum(! se16_ann_tag2name[names  ,'hyp'] == "hypothetical protein") / 10
})
}))

colnames(se_2CS_neib) <- names(dframes)

se_2CS_neib_m <- melt(se_2CS_neib)
```


```{r, fig.height=6, fig.width=6}

g <- ggplot(se_2CS_neib_m,aes(x=variable, y = value)) +
  geom_point(alpha = .75, position = position_jitter()) +
  geom_boxplot() +
  stat_compare_means(ref.group = "Se.comp", label.y = 1,label = "p.signif") +
  theme_prism(axis_text_angle = 45)
g
```


```{r}
se_2CS_neib_counts <- data.frame(lapply(dframes, function(df){
  
  sapply(se_2CS_filtp, function(x){
  r <- sort(df[,x], decreasing=T)
  names <- names(r)[c(1:10)]
  sum(sum(! se16_ann_tag2name[names  ,'hyp'] == "hypothetical protein") > 5)
})
}))

colSums(se_2CS_neib_counts, na.rm=T)
```


# fold change barplots

```{r}

urea_vals <- c(-2.7926333, 
          -4.4748961)
urea_pvals <- c(0.00574318,
           0.00014035)
h2o2_vals <- c(
          -16.183438,
          -4.6980948,
          -3.7242075,
          -2.0944333
          )

h202_pvals <- c(2.35E-33,
           0.00018467,
           0.00890241,
           0.0231164
)

(2**urea_vals)*100

```


```{r}
library(ggprism)
```


```{r}

h2o2_growth <- data.frame(
  gene = c("ctrl","manP","gtfA_2","phoB","g_181"),
  relative_growth = c(100,(2**h2o2_vals)*100)
)

h2o2_growth$gene <- factor(h2o2_growth$gene,
                           levels = c("ctrl","manP","gtfA_2","g_181","phoB"))

g <- ggplot(h2o2_growth, aes(x = gene, y = relative_growth)) +
  geom_bar(stat = "identity", colour=c("black","blue","blue",
                    "darkred","darkred"),
           fill = c("grey","#42ADE2","#42ADE2",
                    "#EE314E","#EE314E"))+
  #coord_trans(y="log10") +
  theme_prism()
g
ggsave("h2o2_barchart.png", height = 3, width = 4.25)

```




# back to heatmap

```{r}


se_2CS_plus <- make.unique(c(se_2CS_filt, ceb$names))
se_2CS_plus_filt <- se_2CS_plus[se_2CS_plus %in% rownames(se_comp_corr)]
se_2CS_names_plus <- se16_ann_tag2name[se_2CS_plus_filt ,'gene_symbol']

se_comp_temp <- se_comp_corr[se_2CS_plus_filt,se_2CS_plus_filt]
rownames(se_comp_temp) <- colnames(se_comp_temp) <-  se_2CS_names_plus

sa_comp_mapped_temp <- sa_comp_mapped_corr[se_2CS_plus_filt,se_2CS_plus_filt]
#rownames(sa_comp_mapped_temp) <- colnames(sa_comp_mapped_temp) <-  se_2CS_names

postFT_model_temp <- postFT_model_corr[se_2CS_plus_filt,se_2CS_plus_filt]
#rownames(postFT_model_temp) <- colnames(postFT_model_temp) <-  se_2CS_names
preFT_model_temp <- preFT_model_corr[se_2CS_plus_filt,se_2CS_plus_filt]
rownames(preFT_model_temp) <- colnames(preFT_model_temp) <-  se_2CS_names_plus



png('corr_spoto_multi_stress_plus.png', res = 600, width = 20, height = 10, units = 'in')
par(mfrow = c(1,2))
corrplot(postFT_model_temp, 
         title='S.e. model post fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

corrplot(preFT_model_temp, 
         title='S.e. model pre fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

dev.off()
```



## Corr plots

```{r}
par(mfrow = c(1,2))

se_2CS_plus <- make.unique(c(se_2CS_filt, ceb$names))
se_2CS_plus_filt <- se_2CS_plus[se_2CS_plus %in% rownames(se_comp_corr)]
se_2CS_names_plus <- se16_ann_tag2name[se_2CS_plus_filt ,'gene_symbol']

se_comp_temp <- se_comp_corr[se_2CS_plus_filt,se_2CS_plus_filt]
rownames(se_comp_temp) <- colnames(se_comp_temp) <-  se_2CS_names_plus

sa_comp_mapped_temp <- sa_comp_mapped_corr[se_2CS_plus_filt,se_2CS_plus_filt]
#rownames(sa_comp_mapped_temp) <- colnames(sa_comp_mapped_temp) <-  se_2CS_names

postFT_model_temp <- postFT_model_corr[se_2CS_plus_filt,se_2CS_plus_filt]
#rownames(postFT_model_temp) <- colnames(postFT_model_temp) <-  se_2CS_names
preFT_model_temp <- preFT_model_corr[se_2CS_plus_filt,se_2CS_plus_filt]
rownames(preFT_model_temp) <- colnames(preFT_model_temp) <-  se_2CS_names_plus



corrplot(se_comp_temp, 
         method = 'color', 
         title='S.e. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)

sa_comp_mapped_temp[is.na(sa_comp_mapped_temp)] <- 0
corrplot(sa_comp_mapped_temp, 
         method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)



```

# zoom in on 102

```{r}

```


```{r}
temp <- ceb$names[ceb$membership == '6']


plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))

#png('net_spoto_multi_stress_with_names.png', res = 600, width = 5, height = 5, units = 'in')
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = .5,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()

```


## net diff


# preFT model nets

```{r, fig.width = 5, fig.height =5}

de_genes <- se_2CS_filt

edges_postFT <- melt(postFT_model_corr) # use with .5
colnames(edges_postFT) <- c('from','to','weight')
edge_postFTs <- edges_postFT[edges_postFT$weight > 0.5,]
de_edges_postFT <- edges_postFT[edges_postFT$weight > 0.5 & 
                                (edges_postFT$from %in% de_genes | edges_postFT$to %in% de_genes),]

#edges <- melt(preFT_model_corr) # use with .5
edges <- melt(se_comp_corr) # use with 0.75

edges_preFT <- melt(preFT_model_corr) # use with 0.5
#edges <- melt(sa_comp_mapped_corr) # use with 0.75
colnames(edges_preFT) <- c('from','to','weight')
edge_preFTs <- edges_preFT[edges_preFT$weight > 0.5,]
de_edges_preFT <- edges_preFT[edges_preFT$weight > 0.5 & 
                                (edges_preFT$from %in% de_genes | edges_preFT$to %in% de_genes),]


net_genes <- union(union(union(union(de_genes, de_edges_preFT$from), 
                         de_edges_preFT$to),de_edges_postFT$from),
                   de_edges_postFT$to)


net_genes_preFT <- union(union(de_genes, de_edges_preFT$from), 
                         de_edges_preFT$to)

net_genes_postFT <- union(union(de_genes, de_edges_postFT$from),
                   de_edges_postFT$to)

net_edges_preFT <- de_edges_preFT
net_edges_preFT <- net_edges_preFT[!is.na(net_edges_preFT$from),]
net_edges_preFT <- net_edges_preFT[!net_edges_preFT$from == net_edges_preFT$to,]

net_edges_postFT <- de_edges_postFT
net_edges_postFT <- net_edges_postFT[!is.na(net_edges_postFT$from),]
net_edges_postFT <- net_edges_postFT[!net_edges_postFT$from == net_edges_postFT$to,]


my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g_preFT <- graph.data.frame(net_edges_preFT[,c(1,2,3)], directed=F)
E(g_preFT)$width <- (net_edges_preFT$weight - min(net_edges_preFT$weight)) / (max(net_edges_preFT$weight) - min(net_edges_preFT$weight))


g_postFT <- graph.data.frame(net_edges_postFT[,c(1,2,3)], directed=F)
E(g_postFT)$width <- (net_edges_postFT$weight - min(net_edges_postFT$weight)) / (max(net_edges_postFT$weight) - min(net_edges_postFT$weight))


g_diff <- difference(g_postFT, g_preFT, byname=T)


bd_g_diff  <- sapply(vertex_attr(g_diff, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})


homs  <- sapply(vertex_attr(g_diff, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2



node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g_diff)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g_diff) 

names <- sapply(vertex_attr(g_diff, 'name'), function(x) se16_ann_tag2name[x,'gene_symbol'])
gene_set <- sapply(vertex_attr(g_diff, 'name'), function(x) if(x %in% se_2CS_filt){'black'}else{'NA'})



sapply(c(1:10), function(x){
  set.seed(x)
  #ceb <- cluster_edge_betweenness(g) 
plot(ceb,g_diff, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     vertex.frame.color = gene_set,
     vertex.size = 10,
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
})



```


## graph match


```{r}
de_genes_se <- se_2CS_filt
de_genes_sa <- sa_2CS_filt

edges_secomp <- melt(se_comp_corr) # use with 0.75
colnames(edges_secomp) <- c('from','to','weight')
edges_secomp <- edges_secomp[edges_secomp$weight > 0.75,]
de_edges_secomp <- edges_secomp[edges_secomp$weight > 0.75 & 
                                (edges_secomp$from %in% de_genes_se | edges_secomp$to %in% de_genes_se),]

#edges <- melt(preFT_model_corr) # use with .5
#edges <- melt(sa_comp_mapped_corr) # use with 0.75
edges_sacomp <- melt(sa_comp_corr) # use with 0.75
colnames(edges_sacomp) <- c('from','to','weight')
edges_sacomp <- edges_sacomp[edges_sacomp$weight > 0.75,]
de_edges_sacomp <- edges_sacomp[edges_sacomp$weight > 0.75 & 
                                (edges_sacomp$from %in% de_genes_sa | edges_sacomp$to %in% de_genes_sa),]



net_edges_secomp <- de_edges_secomp
net_edges_secomp <- net_edges_secomp[!is.na(net_edges_secomp$from),]
net_edges_secomp <- net_edges_secomp[!net_edges_secomp$from == net_edges_secomp$to,]

net_edges_sacomp <- de_edges_sacomp
net_edges_sacomp <- net_edges_sacomp[!is.na(net_edges_sacomp$from),]
net_edges_sacomp <- net_edges_sacomp[!net_edges_sacomp$from == net_edges_sacomp$to,]

g_secomp <- graph.data.frame(net_edges_secomp[,c(1,2,3)], directed=F)
E(g_secomp)$width <- (net_edges_secomp$weight - min(net_edges_secomp$weight)) / (max(net_edges_secomp$weight) - min(net_edges_secomp$weight))


g_sacomp <- graph.data.frame(net_edges_sacomp[,c(1,2,3)], directed=F)
E(g_sacomp)$width <- (net_edges_sacomp$weight - min(net_edges_sacomp$weight)) / (max(net_edges_sacomp$weight) - min(net_edges_sacomp$weight))


g_secomp_cent <- center_graph(g_secomp)
g_sacomp_cent <- center_graph(g_sacomp)

g_sesa_match <- gm(g_secomp_cent, g_sacomp_cent)
```






```{r}
sessionInfo()
```

