---
title: "2024_04_28_gen_nets_sa_se_seqA_n100"
output: powerpoint_presentation
date: "2024-04-28"
---

# Setup

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dev = "png",
  dpi = 600,
  fig.width = 5,
  fig.height = 4
)
```

```{r, warning=F, message=F, include=F}
library(librarian)
shelf(KEGGREST, 
      EnrichmentBrowser,
#      ComplexHeatmap,
#      circlize,
#      RColorBrewer,
#      DESeq2,
      dplyr,
      stringr,
      corrplot,
      XML,
      xml2,
      tidyr,
      dendextend,
      GGally,
      reshape2,
      igraph,
      RColorBrewer,
      gridExtra,
      ggplot2)
#library(KEGGREST)
#library(EnrichmentBrowser)
#library(ComplexHeatmap)
#library(circlize)
#library(RColorBrewer)
#library(DESeq2)
#library(dplyr)
#library(corrplot)
#library(ggplot2)
```

# Load data and models


```{r}

# compendia
sa_comp <- read.csv('../data_files/sa_NCTC3825_filt_norm_log_01.csv')

rownames(sa_comp) <- sa_comp$X
se_names <- read.csv('pandb_b_1282_gene_names.csv',
                     stringsAsFactors = F)
rownames(se_names) <- make.unique(se_names$X1)

sa_comp_mapped <- read.csv('../data_files/prev/sepandb1282_MAPPED_sa_NCTC3825_filt_norm_log_01.csv')

se_names_ordered <- se_names[sa_comp_mapped$X,'X2']
se_names_ordered[is.na(se_names_ordered)] <- sa_comp_mapped$X[is.na(se_names_ordered)]



rownames(sa_comp_mapped) <- se_names_ordered

se_comp <- read.csv('../data_files/prev/se_pandb1282_epi_comp_log_counts_norm_01.csv')
rownames(se_comp) <- se_names_ordered

# TL models

postPT_model <- read.csv('../outputs/weights/prev/data_files/sepandb1282_MAPPED_sa_NCTC3825_filt_norm_log_01_pandb1282_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:relu_init:glorot_normal_ep:10_tied:True_batch:10_lr:0.05_prew:_postPT_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(postPT_model) <- se_names_ordered



postFT_model <- read.csv('../outputs/weights/prev/data_files/sepandb1282_MAPPED_sa_NCTC3825_filt_norm_log_01_pandb1282_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:relu_init:glorot_normal_ep:10_tied:True_batch:10_lr:0.05_prew:_postFT_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(postFT_model) <- se_names_ordered

preFT_model <- read.csv('../outputs/weights/prev/data_files/sepandb1282_MAPPED_sa_NCTC3825_filt_norm_log_01_pandb1282_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:relu_init:glorot_normal_ep:10_tied:True_batch:10_lr:0.05_prew:_preFT_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(preFT_model) <- se_names_ordered


postPTctrl_model <- read.csv('../outputs/weights/prev/data_files/se_pandb1282_epi_comp_log_counts_norm_01_pandb1282_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:relu_init:glorot_normal_ep:10_tied:True_batch:10_lr:0.05_prew:_postPT_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(postPTctrl_model) <- se_names_ordered


postFTctrl_model <- read.csv('../outputs/weights/prev/data_files/se_pandb1282_epi_comp_log_counts_norm_01_pandb1282_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:relu_init:glorot_normal_ep:10_tied:True_batch:10_lr:0.05_prew:_postFT_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(postFTctrl_model) <- se_names_ordered

preFTctrl_model <- read.csv('../outputs/weights/prev/data_files/se_pandb1282_epi_comp_log_counts_norm_01_pandb1282_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:relu_init:glorot_normal_ep:10_tied:True_batch:10_lr:0.05_prew:_preFT_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(preFTctrl_model) <- se_names_ordered


# original models
  seONLY_model <- read.csv('../outputs/weights/prev/data_files/se_pandb1282_epi_comp_log_counts_norm_01_seed:571_nodes:50_kl1:0_kl2:0_act:relu_init:glorot_normal_ep:100_tied:True_batch:10_lr:0.05_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(seONLY_model) <- se_names_ordered


saONLY_model <- read.csv('../outputs/weights/prev/data_files/sepandb1282_MAPPED_sa_NCTC3825_filt_norm_log_01_seed:571_nodes:50_kl1:0_kl2:0_act:relu_init:glorot_normal_ep:100_tied:True_batch:10_lr:0.05_en_weights_da.csv',
                         stringsAsFactors = F,
                         header = F)
rownames(saONLY_model) <- se_names_ordered

```

# Load loss file

```{r}


```



# Load annotations and KEGG pathways

```{r}

se1282_kegg <- read.csv('../node_interpretation/se1282_KEGG_format.txt',
                 stringsAsFactors = F,
                 sep = '\t')
rownames(se1282_kegg) <- se1282_kegg$KEGGPathID

se16_kegg <- read.csv('../node_interpretation/se16_KEGG_format.txt',
                 stringsAsFactors = F,
                 sep = '\t')
rownames(se16_kegg) <- se16_kegg$KEGGPathID

saNCTC8325_kegg <- read.csv('../node_interpretation/saNCTC8325_KEGG_format.txt',
                 stringsAsFactors = F,
                 sep = '\t')
rownames(saNCTC8325_kegg) <- saNCTC8325_kegg$KEGGPathID
```

```{r}

seTU_annotations <- read.csv('Tu3298.gff3', 
                             stringsAsFactors = F,
                             skip = 5,
                             sep = '\t',
                             header=F)
seTU_annotations <- seTU_annotations[seTU_annotations$V3 == "CDS",]

seTU_ann_tag2name <- data.frame(
  locus_tag = sapply(seTU_annotations$V9, 
                            function(x) sub('ID=','',
                                            str_extract(x, 'ID=Tu3298_[0-9]*'))),
  gene_symbol = sapply(seTU_annotations$V9, 
                            function(x) sub('Name=','',
                                            str_extract(x, 'Name=[a-zA-Z0-9_]*'))),
  product = sapply(seTU_annotations$V9, 
                            function(x) sub('product=','',
                                            str_extract(x, 'product=[a-zA-Z0-9_ -//(\\[ ]*')))
)
seTU_ann_tag2name <- seTU_ann_tag2name[!is.na(seTU_ann_tag2name$product),]
rownames(seTU_ann_tag2name) <- make.unique(seTU_ann_tag2name$locus_tag)


se16_annotations <- read.csv('seNIHLM067.gff', 
                             stringsAsFactors = F,
                             skip = 52,
                             sep = '\t',
                             header=F)

se16_ann_tag2name <- data.frame(
  locus_tag = sapply(se16_annotations$V9, 
                            function(x) sub('locus_tag=','',
                                            str_extract(x, 'locus_tag=SE16__[0-9]*'))),
  gene_symbol = sapply(se16_annotations$V9, 
                            function(x) sub('Name=','',
                                            str_extract(x, 'Name=[a-zA-Z0-9_]*'))),
  product = sapply(se16_annotations$V9, 
                            function(x) sub('product=','',
                                            str_extract(x, 'product=[a-zA-Z0-9_ -]*')))
)
se16_ann_tag2name <- se16_ann_tag2name[!is.na(se16_ann_tag2name$product),]
rownames(se16_ann_tag2name) <- se16_ann_tag2name$locus_tag



saNCTC8325_annotations <- read.csv('NCTC8325.gff3', 
                             stringsAsFactors = F,
                             skip = 2,
                             header=F,
                             sep = '\t')

saNCTC8325_ann_tag2name <- data.frame(
  locus_tag = sapply(saNCTC8325_annotations$V9, 
                            function(x) sub('locus_tag=','',
                                            str_extract(x, 'locus_tag=SAOUHSC_[0-9Tp]*'))),
  gene_symbol = sapply(saNCTC8325_annotations$V9, 
                            function(x) sub('Name=','',
                                            str_extract(x, 'Name=[a-zA-Z0-9_]*')))
)

saNCTC8325_ann_name2product <- data.frame(
  gene_symbol = sapply(saNCTC8325_annotations$V9, 
                            function(x) sub('gene=','',
                                            str_extract(x, 'gene=[a-zA-Z0-9_]*'))),
  product = sapply(saNCTC8325_annotations$V9, 
                            function(x) sub('product=','',
                                            str_extract(x, 'product=[a-zA-Z0-9_ -]*')))
)

saNCTC8325_ann_tag2name <- saNCTC8325_ann_tag2name[!is.na(saNCTC8325_ann_tag2name$locus_tag),]
saNCTC8325_ann_name2product <- saNCTC8325_ann_name2product[!is.na(saNCTC8325_ann_name2product$product),]

saNCTC8325_ann_tag2name2 <- merge(saNCTC8325_ann_tag2name,
                                  saNCTC8325_ann_name2product,
                                  all.x = T)


rownames(saNCTC8325_ann_tag2name2) <- make.unique(saNCTC8325_ann_tag2name2$locus_tag)


sepandb1282_annotations <- read.csv('PROKKA_02092022.gff', 
                             stringsAsFactors = F,
                             skip = 43476,
                             header=F,
                             nrows = 17189,
                             sep = '\t')

sepandb1282_ann_tag2name <- data.frame(
  locus_tag = sapply(sepandb1282_annotations$V9, 
                            function(x) sub('locus_tag=','',
                                            str_extract(x, 'locus_tag=KCCCLBPF_[0-9]*'))),
  gene_symbol = sapply(sepandb1282_annotations$V9, 
                            function(x) sub('Name=','',
                                            str_extract(x, 'Name=[a-zA-Z0-9_]*')))
)
sepandb1282_ann_tag2name$locus_tag[is.null(sepandb1282_ann_tag2name$V9 )] <- 'CRISPR'
rownames(sepandb1282_ann_tag2name) <- make.unique(sepandb1282_ann_tag2name$locus_tag)

sepandb1282_ann_name2product <- data.frame(
  gene_symbol = sapply(sepandb1282_annotations$V9, 
                            function(x) sub('gene=','',
                                            str_extract(x, 'gene=[a-zA-Z0-9_]*'))),
  product = sapply(sepandb1282_annotations$V9, 
                            function(x) sub('product=','',
                                            str_extract(x, 'product=[a-zA-Z0-9_ -]*')))
)

sepandb1282_ann_tag2name <- sepandb1282_ann_tag2name[!is.na(sepandb1282_ann_tag2name$locus_tag),]
sepandb1282_ann_name2product <- sepandb1282_ann_name2product[!is.na(sepandb1282_ann_name2product$product),]

sepandb1282_ann_tag2name2 <- merge(sepandb1282_ann_tag2name,
                                  sepandb1282_ann_name2product,
                                  all.x = T)


rownames(sepandb1282_ann_tag2name2) <- make.unique(sepandb1282_ann_tag2name2$locus_tag)



```

```{r}
se_sa_map <- read.csv('se16_sa3825_map.csv',
                      stringsAsFactors = F)
sepandb1282_tu3298_map <- read.csv('seTU3298_to_pandb1282_dcmegab_best_hits.csv',
                      stringsAsFactors = F,
                      header = F,
                      sep='@')

sepandb1282_tu3298_map_ordered <- sepandb1282_tu3298_map[order(sepandb1282_tu3298_map$V3),]

rownames(sepandb1282_tu3298_map_ordered) <- make.unique(sepandb1282_tu3298_map_ordered $V2)
```



# Gene-gene correlations

```{r}
corr_method <- 'pearson' # pearson, kendall, spearman
sa_comp_corr <- cor(t(sa_comp[,-1]), method = corr_method) 
rownames(sa_comp_corr)  <- sa_comp$X
colnames(sa_comp_corr)  <- sa_comp$X

sa_comp_mapped_corr <- cor(t(sa_comp_mapped[,-1]), method = corr_method)
rownames(sa_comp_mapped_corr)  <- se_names_ordered
colnames(sa_comp_mapped_corr)  <- se_names_ordered

se_comp_corr <- cor(t(se_comp[,-1]), method = corr_method)
rownames(se_comp_corr)  <- se_names_ordered
colnames(se_comp_corr)  <- se_names_ordered

postFT_model_corr <- cor(t(postFT_model), method = corr_method)
rownames(postFT_model_corr)  <- se_names_ordered
colnames(postFT_model_corr)  <- se_names_ordered

preFT_model_corr <- cor(t(preFT_model), method = corr_method)
rownames(preFT_model_corr)  <- se_names_ordered
colnames(preFT_model_corr)  <- se_names_ordered

se_model_corr <- cor(t(seONLY_model), method = corr_method)
rownames(se_model_corr)  <- se_names_ordered
colnames(se_model_corr)  <- se_names_ordered

sa_model_corr <- cor(t(saONLY_model), method = corr_method)
rownames(sa_model_corr)  <- se_names_ordered
colnames(sa_model_corr)  <- se_names_ordered
```


```{r}
par(mfrow = c(1,2))

corrplot(se_comp_corr[1:10,1:10], 
         method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

corrplot(sa_comp_corr[1:10,1:10], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)
```


```{r}
par(mfrow = c(1,2))

corrplot(se_comp_corr[1:100,1:100], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

corrplot(sa_comp_corr[1:100,1:100], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)
```


```{r}
par(mfrow = c(1,2))

corrplot(sa_comp_corr[1:100,1:100], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

corrplot(sa_comp_mapped_corr[1:100,1:100], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)
```


```{r}
par(mfrow = c(1,2))

corrplot(se_comp_corr[1:100,1:100], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

corrplot(sa_comp_mapped_corr[1:100,1:100], method = 'color', 
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)
```



```{r}
par(mfrow = c(2,2))

corrplot(se_comp_corr[1:100,1:100], method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

corrplot(sa_comp_mapped_corr[1:100,1:100], method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
          tl.pos = 'n',
         diag = FALSE)

corrplot(se_model_corr[1:100,1:100], method = 'color', 
         title='S.e. model', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.pos = 'n',
         diag = FALSE)

corrplot(sa_model_corr[1:100,1:100], method = 'color', 
         title='S.a. model', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.pos = 'n',
         diag = FALSE)

```

```{r}
par(mfrow = c(2,2))



corrplot(se_model_corr[1:100,1:100], method = 'color', 
         title='S.e. model', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.pos = 'n',
         diag = FALSE)

corrplot(sa_model_corr[1:100,1:100], method = 'color', 
         title='S.a. model', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.pos = 'n',
         diag = FALSE)

corrplot(postFT_model_corr[1:100,1:100], method = 'color', 
         title='S.e. model post fine-tune', 
         mar=c(0,0,1,0),
         
         tl.pos = 'n',
         order = 'original', diag = FALSE)

corrplot(preFT_model_corr[1:100,1:100], method = 'color', 
         title='S.e. model pre fine-tune', 
         mar=c(0,0,1,0),
         tl.pos = 'n',
         order = 'original', diag = FALSE)
```




```{r}

```



# Plot by KEGG pathway

```{r}
se_2CS <- unlist(str_split(se1282_kegg['map02020:Two-component system', 'Genes'],
                    pattern = ';'))
se_2CS_filt <- se_2CS[se_2CS %in%rownames(postFT_model_corr)]


sa_2CS <- unlist(str_split(saNCTC8325_kegg['sao02020:Two-component system - Staphylococcus aureus subsp. aureus NCTC8325', 'Genes'],
                    pattern = ';'))

sa_2CS_filt <- sa_2CS[sa_2CS %in%rownames(sa_model_corr)]

```










# Tangles








### Tangle of compendium vs model

```{r}
rands <- sample(rownames(se_comp), 50, replace=F)
homs <- sapply(rands,
       function(x) max(sa_comp_mapped[x,-1])) > 0

d1 <- postFT_model[rands,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()
d2 <- se_comp[rands,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()

d3 <- d2 %>% match_order_by_labels(d1)


# Custom these kendo, and place them in a list
dl <- dendlist(
  d1 %>% 
    set("labels_col", as.numeric(homs)+1) %>%
    set("branches_lty", 1) ,
  d2 %>% 
    set("labels_col",  as.numeric(homs)+1)  %>%
    set("branches_lty", 1) 
)
 
dl  %>% entanglement

dl_unt <- dl %>% untangle(method = "step1side") 
dl_unt %>% entanglement
tanglegram(dl_unt, 
           common_subtrees_color_lines = TRUE, 
           common_subtrees_color_branches = TRUE,
           highlight_distinct_edges  = TRUE, 
           highlight_branches_lwd=FALSE, 
           margin_inner=7,
           lwd=2,
           main_left = "post ft ",
           main_right = "se comp",
           match_order_by_labels = TRUE
)
```

### KEGG paths

```{r}
tangle_kegg <- function(se_path){
  
  se_2CS <- unlist(str_split(se16_kegg[se_path, 'Genes'],
                    pattern = ';'))
se_2CS_filt <- se_2CS[se_2CS %in%rownames(postFT_model_corr)]


  homs <- sapply(se_2CS_filt,
       function(x) max(sa_comp_mapped[x,-1])) > 0

d1 <- postFT_model[se_2CS_filt,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()
d2 <- preFT_model[se_2CS_filt,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()

d3 <- d2 %>% match_order_by_labels(d1)


# Custom these kendo, and place them in a list
dl <- dendlist(
  d1 %>% 
    set("labels_col", as.numeric(homs)+1) %>%
    set("branches_lty", 1) ,
  d2 %>% 
    set("labels_col",  as.numeric(homs)+1)  %>%
    set("branches_lty", 1) 
)
 

dl  %>% entanglement

# Plot them together
name_safe <- sub('/','_',sub(':','_',sub(' ','_',se_path)))

png(paste(c('tangles/t_',name_safe,'.png'), collapse=''), res = 600, width = 5, height = 5, units = 'in')
  par(mfrow = c(2,2))
tanglegram(dl, 
           common_subtrees_color_lines = TRUE, 
           common_subtrees_color_branches = TRUE,
           highlight_distinct_edges  = TRUE, 
           highlight_branches_lwd=FALSE, 
           margin_inner=7,
           lwd=2,
           match_order_by_labels = TRUE
)
dev.off()
}
```

```{r}
se_kegg_m2 <- se1282_kegg$KEGGPathID[se1282_kegg$Length > 2]

#tangles <- lapply(se_kegg_m2, function(x) tangle_kegg(x))
```


# As nets

Gene-gene nets can show correlation results with visual interpretation:

- edge weight is gene-gene correlation in the data matrix or model weights
- node color is e value from homolog mapping
- node outline is whether gene is in pathway being plotted

```{r}
edges <- melt(se_comp_corr)
colnames(edges) <- c('from','to','weight')
edges <- edges[edges$weight > 0.4,]
de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.8 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]

net_edges <- net_edges[!net_edges$from == net_edges$to,]
```

```{r}
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight * 20)-10

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})


homs  <- sapply(vertex_attr(g, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2

node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]


plot(g, vertex.label = NA, vertex.frame.color = bd)
```

```{r}
ceb <- cluster_edge_betweenness(g) 
```

```{r}
plot(ceb, g, 
     vertex.label = NA, 
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
```


```{r}
plot_nets <- function(se_path){
se_2CS <- unlist(str_split(se1282_kegg[se_path, 'Genes'],
                    pattern = ';'))
se_2CS_filt <- se_2CS[se_2CS %in%rownames(postFT_model_corr)]

de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.95 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]
net_edges <- net_edges[!net_edges$from == net_edges$to,]


my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight * 30)-29

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){'black'}else{'grey'})


homs  <- sapply(vertex_attr(g, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2

node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g) 
name_safe <- sub('/','_',sub(':','_',sub(' ','_',se_path)))

#png(paste(c('net_plots/',name_safe,'.png'), collapse=''), res = 600, width = 5, height = 5, units = 'in')
plot(ceb, g, 
     vertex.label = NA, 
     col = vertex_attr(g, 'color'), 
     vertex.frame.color = bd,
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()

names <- sapply(vertex_attr(g, 'name'), function(x) se16_ann_tag2name[x,'gene_symbol'])

#png(paste(c('net_plots/',name_safe,'_names.png'), collapse=''), res = 600, width = 5, height = 5, units = 'in')
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
    col = vertex_attr(g, 'color'), 
     vertex.frame.color = bd,
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()
}
```

```{r}
se_kegg_m2 <- se16_kegg$KEGGPathID[se16_kegg$Length > 2]

#nets <- lapply(se_kegg_m2, function(x) plot_nets(x))
```




```{r}
#lapply(se_kegg_m2[57], function(x) plot_nets(x))

se_path <- se_kegg_m2[57]
se_2CS <- unlist(str_split(se16_kegg[se_path, 'Genes'],
                    pattern = ';'))
se_2CS_filt <- se_2CS[se_2CS %in%rownames(postFT_model_corr)]

de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.75 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]
net_edges <- net_edges[!net_edges$from == net_edges$to,]


my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight * 30)-29

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})

rownames(sepandb1282_tu_map) <- make.unique(sepandb1282_tu_map$V2)
g_tu_names <- sepandb1282_tu_map[vertex_attr(g, 'name'), "V1"]
rownames(se16_tu_map) <- make.unique(se16_tu_map$tu3298_ID)
g_16_names <- se16_tu_map[g_tu_names, "se16_ID"]

homs  <- sapply(g_16_names, function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2

node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g) 


plot(ceb, g, 
     vertex.label = NA, 
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
```


# Michelle's stress response genes

```{r}
spoto_stress <- read.csv('spoto_stress_genes.csv', stringsAsFactors = F)
se16_tu_map <- read.csv('se16_tu3298_map.csv', stringsAsFactors = F)
sepandb1282_tu_map <- read.csv('seTU3298_to_pandb1282_dcmegab_best_hits.csv', 
                               stringsAsFactors = F,
                               sep='@',
                               header=F)

spoto_stress_se16 <- unique(se16_tu_map$se16_ID[se16_tu_map$tu3298_ID %in% spoto_stress$Tu3298.ID])

spoto_stress_sepandb1282 <- unique(sepandb1282_tu_map$V2[sepandb1282_tu_map$V1 %in% spoto_stress$Tu3298.ID])

spoto_stress_sepandb1282_names <- se_names[spoto_stress_sepandb1282, 'X2']

se_2CS_filt <- c(spoto_stress_sepandb1282[spoto_stress_sepandb1282 %in%rownames(se_model_corr)],
                 spoto_stress_sepandb1282_names[spoto_stress_sepandb1282_names %in%rownames(se_model_corr)])

```



```{r, fig.height=8, fig.width=8}
par(mfrow = c(3,2))



spoto_stress_sepandb1282_filt <- spoto_stress_sepandb1282[spoto_stress_sepandb1282 %in% se_comp$X]
spoto_stress_sepandb1282_filt_tu <- sepandb1282_tu3298_map_ordered[spoto_stress_sepandb1282_filt, 'V1']
se_2CS_names <- seTU_ann_tag2name[spoto_stress_sepandb1282_filt_tu ,'product']

se_comp_temp <- se_comp_corr
rownames(se_comp_temp) <- colnames(se_comp_temp) <- se_comp$X
se_comp_temp <- se_comp_temp[spoto_stress_sepandb1282_filt, spoto_stress_sepandb1282_filt]
rownames(se_comp_temp) <- colnames(se_comp_temp) <-  spoto_stress_sepandb1282_filt_tu

sa_comp_mapped_temp <- sa_comp_mapped_corr
rownames(sa_comp_mapped_temp) <- colnames(sa_comp_mapped_temp) <- se_comp$X
sa_comp_mapped_temp <- sa_comp_mapped_temp[spoto_stress_sepandb1282_filt,spoto_stress_sepandb1282_filt]
rownames(sa_comp_mapped_temp) <- colnames(sa_comp_mapped_temp) <-  spoto_stress_sepandb1282_filt_tu

postFT_model_temp <- postFT_model_corr
rownames(postFT_model_temp) <- colnames(postFT_model_temp) <- se_comp$X
postFT_model_temp <- postFT_model_temp[spoto_stress_sepandb1282_filt,spoto_stress_sepandb1282_filt]
rownames(postFT_model_temp) <- colnames(postFT_model_temp) <-  spoto_stress_sepandb1282_filt_tu

preFT_model_temp <- preFT_model_corr
rownames(preFT_model_temp) <- colnames(preFT_model_temp) <- se_comp$X
preFT_model_temp <- preFT_model_temp[spoto_stress_sepandb1282_filt,spoto_stress_sepandb1282_filt]
rownames(preFT_model_temp) <- colnames(preFT_model_temp) <-  spoto_stress_sepandb1282_filt_tu

se_model_temp <- se_model_corr
rownames(se_model_temp) <- colnames(se_model_temp) <- se_comp$X
se_model_temp <- se_model_temp[spoto_stress_sepandb1282_filt,spoto_stress_sepandb1282_filt]
rownames(se_model_temp) <- colnames(se_model_temp) <-  spoto_stress_sepandb1282_filt_tu

sa_model_temp <- sa_model_corr
rownames(sa_model_temp) <- colnames(sa_model_temp) <- se_comp$X
sa_model_temp <- sa_model_temp[spoto_stress_sepandb1282_filt,spoto_stress_sepandb1282_filt]
rownames(sa_model_temp) <- colnames(sa_model_temp) <-  spoto_stress_sepandb1282_filt_tu


corrplot(se_comp_temp, 
         method = 'color', 
         title='S.e. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)

sa_comp_mapped_temp[is.na(sa_comp_mapped_temp)] <- 0
corrplot(sa_comp_mapped_temp, 
         method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)


corrplot(postFT_model_temp, 
         title='S.e. model post fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

corrplot(preFT_model_temp, 
         title='S.e. model pre fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

corrplot(se_model_temp, 
         title='S.e. model ', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

corrplot(sa_model_temp, 
         title='S.a. model ', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)
```


```{r}
#png(paste(c('corrplots_spoto_multi_stress_sepanDB1282','.png'), collapse=''), res = 600, width = 10, height = 12, units = 'in')



par(mfrow = c(3,2))
corrplot(se_comp_temp, 
         method = 'color', 
         title='S.e. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)

sa_comp_mapped_temp[is.na(sa_comp_mapped_temp)] <- 0
corrplot(sa_comp_mapped_temp, 
         method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)

corrplot(se_model_temp, 
         title='S.e. model ', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

corrplot(sa_model_temp, 
         title='S.a. model ', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

corrplot(postFT_model_temp, 
         title='S.e. model post fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

corrplot(preFT_model_temp, 
         title='S.e. model pre fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)



#dev.off()
```


```{r}
#png(paste(c('corrplots_spoto_multi_stress_sepanDB1282_names','.png'), collapse=''), res = 600, width = 15, height = 15, units = 'in')

rownames(se_comp_temp) <- colnames(se_comp_temp) <-  se_2CS_names
rownames(sa_comp_mapped_temp) <- colnames(sa_comp_mapped_temp) <-  se_2CS_names
rownames(postFT_model_temp) <- colnames(postFT_model_temp) <-  se_2CS_names
rownames(preFT_model_temp) <- colnames(preFT_model_temp) <-  se_2CS_names

par(mfrow = c(2,2))

se_comp_temp[is.na(se_comp_temp)] <- 0
corrplot(se_comp_temp, 
         method = 'color', 
         title='S.e. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)

sa_comp_mapped_temp[is.na(sa_comp_mapped_temp)] <- 0
corrplot(sa_comp_mapped_temp, 
         method = 'color', 
         title='S.a. comp', 
         mar=c(0,0,1,0),
         order = 'original', 
         tl.cex = 0.3,
         tl.col = 'black',
         diag = FALSE)


corrplot(postFT_model_temp, 
         title='S.e. model post fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

corrplot(preFT_model_temp, 
         title='S.e. model pre fine-tune', 
         mar=c(0,0,1,0),
         method = 'color', 
         order = 'hclust', 
         diag = FALSE,
         tl.col = 'black',
         tl.cex = 0.3)

#dev.off()
```


```{r}

postFT_model_temp <- postFT_model
preFT_model_temp <- preFT_model

rownames(postFT_model_temp) <- se_comp$X
rownames(preFT_model_temp) <- se_comp$X

sa_comp_mapped_temp <- sa_comp_mapped
rownames(sa_comp_mapped_temp)  <- se_comp$X

homs <- sapply(spoto_stress_sepandb1282_filt,
       function(x) max(sa_comp_mapped_temp[x,-1])) > 0

d1 <- postFT_model_temp[spoto_stress_sepandb1282_filt,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()
d2 <- preFT_model_temp[spoto_stress_sepandb1282_filt,] %>% dist() %>% hclust( method="complete" ) %>% as.dendrogram()

d3 <- d1 %>% match_order_by_labels(d2)


# Custom these kendo, and place them in a list
dl <- dendlist(
  d2 %>% 
    set("labels_col",  as.numeric(homs)+1)  %>%
    set("branches_lty", 1) ,
  d1 %>% 
    set("labels_col", as.numeric(homs)+1) %>%
    set("branches_lty", 1)
)
 

dl  %>% entanglement

# Plot them together
#name_safe <- sub('/','_',sub(':','_',sub(' ','_',se_path)))

#png(paste(c('tangles/t_','spoto_multi_stress_sepanDB1282','.png'), collapse=''), res = 600, width = 5, height = 5, units = 'in')
tanglegram(dl, 
           common_subtrees_color_lines = TRUE, 
           common_subtrees_color_branches = TRUE,
           highlight_distinct_edges  = TRUE, 
           highlight_branches_lwd=FALSE, 
           margin_inner=7,
           lwd=2,
           match_order_by_labels = TRUE
)
#dev.off()
```

```{r}
de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.999 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]

net_edges <- net_edges[!net_edges$from == net_edges$to,]

my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight * 20)-10

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})


homs  <- sapply(vertex_attr(g, 'name'), function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2



node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g) 

names <- sapply(vertex_attr(g, 'name'), function(x) se16_ann_tag2name[x,'gene_symbol'])

plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
```




```{r}
de_genes <- se_2CS_filt

de_edges <- edges[edges$weight > 0.999 & (edges$from %in% de_genes | edges$to %in% de_genes),]

net_genes <- union(union(de_genes, de_edges$from), de_edges$to)
net_edges <- de_edges
net_edges <- net_edges[!is.na(net_edges$from),]

net_edges <- net_edges[!net_edges$from == net_edges$to,]

my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 700)

g <- graph.data.frame(net_edges[,c(1,2,3)], directed=F)
E(g)$width <- (net_edges$weight * 20)-10

bd  <- sapply(vertex_attr(g, 'name'), function(x) if(x %in% de_genes){if(x %in% de_genes){'black'}else{'yellow'}}else{if(x %in% de_genes){'grey'}else{'white'}})

rownames(sepandb1282_tu_map) <- make.unique(sepandb1282_tu_map$V2)
g_tu_names <- sepandb1282_tu_map[vertex_attr(g, 'name'), "V1"]
rownames(se16_tu_map) <- make.unique(se16_tu_map$tu3298_ID)
g_16_names <- se16_tu_map[g_tu_names, "se16_ID"]
homs  <- sapply(g_16_names, function(x) -log(min(se_sa_map[se_sa_map$se16_ID == x, 'hit_evalue'], na.rm=T)))
homs[homs == -Inf] <- 0
homs[homs == Inf] <- max(homs[! homs == Inf]) * 2



node.colors <- (homs + max(homs)) / (2*max(homs)) * 700
V(g)$color <- my_palette[node.colors]

ceb <- cluster_edge_betweenness(g) 

names <- sapply(vertex_attr(g, 'name'), function(x) se16_ann_tag2name[x,'gene_symbol'])

plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))

#png('net_spoto_multi_stress_with_names_panDB1282.png', res = 600, width = 5, height = 5, units = 'in')
plot(ceb, g, 
     vertex.label = names, 
     vertex.label.cex = .5,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()

```

```{r}
plot(ceb, g, 
     vertex.label = NA, 
     vertex.label.cex = .3,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
```

```{r}
rownames(se16_tu_map) <- make.unique(se16_tu_map$se16_ID)
names_tu <- sapply(g_16_names, function(x) se16_tu_map[x ,'tu3298_ID'])

names_tu <- g_tu_names
#png('net_spoto_multi_stress_with_names_tu.png', res = 600, width = 5, height = 5, units = 'in')
plot(ceb, g, 
     vertex.label = names_tu, 
     vertex.label.cex = .5,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()

goi <- c('Tu3298_108','Tu3298_116','Tu3298_181',
         'Tu3298_779','Tu3298_2157','Tu3298_116',
         'Tu3298_2208')
names_tu[!names_tu %in% goi] <- NA
#png('net_spoto_multi_stress_with_names_tu_select.png', res = 600, width = 5, height = 5, units = 'in')
plot(ceb, g, 
     vertex.label = names_tu, 
     vertex.label.cex = .5,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()

#png('net_spoto_multi_stress.png', res = 600, width = 5, height = 5, units = 'in')
plot(ceb, g, 
     vertex.label = NA, 
     vertex.label.cex = .5,
     vertex.label.color = 'black',
     #vertex.label.dist=2,
     col = vertex_attr(g, 'color'), 
     mark.coly = brewer.pal(n = 8, name = "Set3"))
#dev.off()
```


```{r}
sessionInfo()
```

